---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

library(emoji)

Title <- "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
Authors <- "Andrew Heiss and Meng Ye"
Year <- "2022"
```

# `r Title`

[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University  
Meng Ye • Andrew Young School of Policy Studies • Georgia State University

---

## Abstract

China's 2016 Overseas NGO (ONGO) Law is part of a larger global trend of increased legal restrictions on international nongovernmental organizations (INGOs). A growing body of research analyzes the broad effects of this crackdown on INGOs, finding a divergence in formal *de jure* laws and the *de facto* implementation of those laws. The causes and mechanisms of this divergence remain less explored. Why do authoritarian governments allow—and often collaborate—with some INGOs while harshly regulating or expelling others? What determines the openness of the practical legal operating environment for INGOs? In this paper, we use the case of China to explore how political demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the ONGO Law came into effect. We argue that in an effort to bolster regime stability, governments use civil society laws as policy tools to influence INGO behavior. We find that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs. We test this argument with a mixed methods research design, combining Bayesian analysis of administrative data from all formally registered INGOs with a comparative case study of two environmental INGOs. Our findings offer insights into the practical effects of INGO restrictions and the dynamics of closing civic space worldwide.

---

## `r emoji::emoji_glue(":hugs::oyster:")`: "Compassionate clam" project name

Because project titles change all the time with revisions, rewriting, and peer review, we used [**codename**](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won't change.

```{r generate-code-name, eval=FALSE}
library(codename)
codename_message()
#> code name generated by {codename} v.0.4.0

codename(seed = "china ongo law", type = "ubuntu")
#> [1] "compassionate clam"
```

## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))

**Code:** All code is licensed under the [MIT License](LICENSE.md).

## Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
