---
title: >-
  Online appendix for "Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society"
short-title: 'Online appendix for "Enforcing Boundaries"'
date: "2023-12-07"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.json
link-citations: true
---

```{r setup, include=FALSE}
if (is.null(knitr::pandoc_to())) {
  fmt_out <- "interactive"
} else {
  fmt_out <- knitr::pandoc_to()
}

knitr::opts_chunk$set(
  echo = FALSE, include = FALSE,
  warning = FALSE, message = FALSE
)

knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "100%", collapse = TRUE
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-data}
library(tidyverse)
library(scales)
library(modelsummary)
library(tinytable)
library(targets)

# Generated via random.org
set.seed(8511)

# Targets stuff
tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)
 
tar_load(c(models_tbl))

# Plotting and modelsummary functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))

theme_set(theme_ongo())
set_annotation_fonts()
```

# Model details and results

We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-1 v4.3.1] and **brms** [@Burkner:2017 v2.20.5] to estimate our ordered Beta regression models [@Kubinec:2022]. We simulate 4 MCMC chains with 2,000 draws in each chain, 1,000 of which are used for warmup, resulting in 4,000 (1,000 × 4) draws per model parameter. We assess convergence with visual inspection, and all chains converge. Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and model diagnostics—as well as our code and data—are available `ANONYMIZED_URL`. We include the formal definition and priors for our model below.

$$
\begin{aligned}
&\ \textbf{Registered provinces for INGO } i \\
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
&\ \textbf{Model of outcome average} \\
\mu_i =&\ 
  \mathrlap{\begin{aligned}[t]
  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
  \end{aligned}}\\[8pt]
&\ \textbf{Priors} \\
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
\end{aligned}
$$

\newpage

```{r}
#| label: tbl-coefs-orig
#| tbl-cap: "Complete model coefficients"
#| include: true

notes <- paste(
  "Estimates are median posterior log odds from ordered Beta regression models;",
  "95% credible intervals (highest density posterior interval, or HDPI) in brackets."
)

if (fmt_out == "latex") {
  notes <- str_replace_all(notes, "%", r"(\\%)")
}

inner <- "
row{odd[3-35]}={abovesep=0pt, belowsep=2pt},
row{even[4-36]}={rowsep=0pt},
cells={font=\\footnotesize}, row{1}={valign=b}
"

modelsummary(
  models_tbl$msl,
  estimate = "{estimate}",
  statistic = "[{conf.low}, {conf.high}]",
  fmt = fmt_significant(2),
  coef_map = models_tbl$nice_coefs,
  notes = c(notes),
  width = c(50, 25, 25),
  output = "tinytable"
) |>
  style_tt(j = 2:3, align = "c") |>
  style_tt(i = seq(1, 35, 2), j = 1, rowspan = 2, alignv = "t") |>
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  )
```

\clearpage

# Coding rules for issue ares

Author 1 assigned each organization to one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases. Organizations with multiple ROs are coded based on the overall issue area of the INGO, not the specific RO, so to ensure the issue area coding is consistent across ROs.

We followed these rules for categorizing INGOs' stated missions into issue areas:

- **Education vs. Charity and humanitarian**: If charitable activities are all education related (e.g., building schools, donating education facilities and books), code as *Education*. If activities include other community support (e.g., building bridges, roads, medical facilities), code as *Charity and humanitarian*.
- **Economy and trade vs. Industry association**: If the trade promoted is focused on a particular industry (e.g., poultry, grains, etc.), code as *Industry association*.
- **Arts and culture**: Include sports organizations.
- **Industry association vs. Health & Science and technology & Arts and culture**: There are professional associations for health providers, scientific associations, and artistic industries. If activities go beyond only serving members only, code as *Health* or *Science and technology* or *Arts and culture*; if activities are limited to member-only service, code as *Industry association*.
- **Health vs. Charity and humanitarian**: If activities only provide medical assistance to underprivileged communities, code as *Health*.
- **Charity and humanitarian vs. General**: If there are overlapping issue areas (e.g., poverty alleviation, education, health), code as *General*, then code the apparent primary issue area as a second work area.


# Comparison of the cases of TNC and Greenpeace

@tbl-case-study summarizes the cases of TNC and Greenpeace. In addition to confirming the correlation between issue area and operational space found in the statistical model, the cases highlight how government preferences exert influence on both the degree of contentious programming INGOs are allowed to undertake and the severity of legal restrictions INGOs can face.

```{r}
#| label: tbl-case-study
#| tbl-cap: "Comparison of the work of The Nature Conservancy and Greenpeace in China"
#| include: true

compare_table <- read_csv(here::here("data", "manual_data", "table-case-study.csv"))

compare_table |>
  rename(` ` = Characteristic) |>
  tt(
    width = c(20, 30, 30)
  ) |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(j = 1:3, align = "l") |>
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = "rowsep=1pt, cells={font=\\footnotesize}"
  )
```


\newpage

# References

::: {#refs .bibliography}
:::
