---
title: "Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law"
short-title: "Operational constraints and closing civic space"
date: "2023-12-03"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
abstract: |
  TODO: **Update this based on the finished version of the paper.** China’s 2016 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs). However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws. Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations. In this paper, we explore the effect of China’s ONGO law on INGO operations in the five years since the passage of the law. We test whether and how INGO operational space under the ONGO law is influenced by organizations' issue areas. We argue that the less contentious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in. China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2016 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities. We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with a multilevel Bayesian model. Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
keywords:
  - international NGOs
  - civil society
  - authoritarianism
  - Chinese ONGO law
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.bib
link-citations: true
toc-depth: 4
---

```{r setup, include=FALSE}
if (is.null(knitr::pandoc_to())) {
  fmt_out <- "interactive"
} else {
  fmt_out <- knitr::pandoc_to()
}

knitr::opts_chunk$set(
  echo = FALSE, include = FALSE,
  warning = FALSE, message = FALSE
)

knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "100%", collapse = TRUE
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-data}
library(tidyverse)
library(sf)
library(scales)
library(tidybayes)
library(ggrepel)
library(marginaleffects)
library(tidygraph)
library(ggraph)
library(patchwork)
library(glue)
library(janitor)
library(gt)
library(targets)

# Generated via random.org
set.seed(8511)

# Targets stuff
tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)
 
tar_load(c(ongo, ongo_mapdata, civicus_clean))
tar_load(c(
  preds_issue, preds_local, preds_timing,
  epreds_issue, epreds_local, epreds_timing,
  epreds_timing_local, issue_indicator_lookup
))
tar_load(c(preds_issue_plot, preds_local_plot, preds_timing_plot))

# Plotting and modelsummary functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

theme_set(theme_ongo())
set_annotation_fonts()
```

```{r civicus-stuff}
civicus_prop <- civicus_clean |> 
  group_by(open = Score > 80) |> 
  summarize(total = n()) |> 
  mutate(
    prop = total / sum(total),
    prop_nice = label_percent(accuracy = 1)(prop)
  ) |> 
  mutate(open = make_clean_names(open)) |> 
  split(~open)
```

```{r calc-provinces}
provinces <- ongo_mapdata |> 
  drop_na(province_code) |> 
  st_drop_geometry() |> 
  mutate(rank = dense_rank(-ro_count)) |> 
  mutate(list_name = make_clean_names(province_en)) |> 
  split(~ list_name)

# Get the RO count for the 4th-ranked province
province4th <- provinces |> 
  map(~filter(.x, rank == 4)) |> 
  keep(~nrow(.x) > 0)
```

```{r calc-issues}
# MAYBE: Use issue_area instead of work_field_code
issue_count <- ongo |> 
  drop_na(work_field_code1) |> 
  group_by(work_field_code1) |>
  summarize(n = n()) |> 
  mutate(work_field_code1 = fct_reorder(work_field_code1, n))

issues <- issue_count |> 
  mutate(prop = n / sum(n)) |> 
  mutate(prop_nice = label_percent(accuracy = 1)(prop)) |> 
  mutate(work_field_code1 = make_clean_names(work_field_code1)) |> 
  split(~ work_field_code1)

preds_issue_plot_order <- preds_issue_plot |> 
  filter(outcome == "All 32 provinces") |>
  group_by(issue_area_nice) |> 
  summarize(median_prop = median(prop)) |> 
  arrange(median_prop) |> 
  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
  mutate(issue_area_nice = fct_inorder(issue_area_nice))

preds_issue_text <- preds_issue_plot |> 
  group_by(outcome, issue_area_nice) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  group_by(issue_area_nice) |> 
  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
  mutate(y_plot = 1 - y_plot) |> 
  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
  mutate(prop_ci_nice = glue::glue(
    "{ymin}–{ymax}",
    ymin = label_number(accuracy = 1, scale = 100)(ymin),
    ymax = label_percent(accuracy = 1)(ymax)
  )) |> 
  mutate(issue_area_nice = factor(
    issue_area_nice, 
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  ))

p_issue <- preds_issue_text |> 
  mutate(issue_area_nice = make_clean_names(issue_area_nice, allow_dupes = TRUE)) |> 
  mutate(outcome = make_clean_names(outcome, allow_dupes = TRUE)) |> 
  ungroup() |> 
  split(~ issue_area_nice + outcome)

c_issue <- epreds_issue |> 
  group_by(issue_area) |> 
  mutate(count = prop_to_provinces(.epred)) |> 
  median_qi(count) |> 
  mutate(across(c(.lower, .upper), list(whole = ~round(., 0)))) |> 
  mutate(count_median = round(count, 0)) |> 
  mutate(range = glue("{.lower_whole}–{.upper_whole}")) |> 
  split(~ issue_area)
```

```{r calc-local-connections}
loc <- ongo |> 
  count(local_connect) |> 
  mutate(
    prop = n / sum(n),
    prop_nice = label_percent(accuracy = 1)(prop)
  ) |> 
  mutate(local_connect = make_clean_names(local_connect)) |> 
  split(~ local_connect)

preds_local_text <- preds_local_plot |> 
  group_by(outcome, local_connect) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  group_by(local_connect) |> 
  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
  mutate(y_plot = 1 - y_plot) |> 
  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
  mutate(prop_ci_nice = glue::glue(
    "{ymin}–{ymax}",
    ymin = label_number(accuracy = 1, scale = 100)(ymin),
    ymax = label_percent(accuracy = 1)(ymax)
  ))

p_loc <- preds_local_text |> 
  mutate(local_connect = make_clean_names(local_connect, allow_dupes = TRUE)) |> 
  mutate(outcome = make_clean_names(outcome, allow_dupes = TRUE)) |> 
  ungroup() |> 
  split(~ local_connect + outcome)

c_local <- epreds_local |> 
  mutate(local_connect = case_match(local_connect, TRUE ~ "true", FALSE ~ "false")) |> 
  group_by(local_connect) |> 
  mutate(count = prop_to_provinces(.epred)) |> 
  median_qi(count) |> 
  mutate(across(c(.lower, .upper), list(whole = ~round(., 0)))) |> 
  mutate(count_median = round(count, 0)) |> 
  mutate(range = glue("{.lower_whole}–{.upper_whole}")) |> 
  split(~ local_connect)
```

```{r calc-timing}
ros_2017 <- ongo |> 
  count(pre_2018 = registration_date < ymd("2018-01-01")) |> 
  mutate(
    prop = n / sum(n),
    prop_nice = label_percent(accuracy = 1)(prop)
  ) |> 
  filter(pre_2018 == TRUE) |> 
  as.list()

p_timing <- preds_timing_plot |> 
  filter(years_since_law %in% c(2017, 2022)) |> 
  group_by(years_since_law, outcome) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
  mutate(prop_ci_nice = glue::glue(
    "{ymin}–{ymax}",
    ymin = label_number(accuracy = 1, scale = 100)(ymin),
    ymax = label_percent(accuracy = 1)(ymax)
  )) |> 
  group_by(outcome) |> 
  mutate(years_since_law = make_clean_names(years_since_law)) |> 
  group_by(years_since_law) |> 
  mutate(outcome = make_clean_names(outcome)) |> 
  ungroup() |> 
  split(~ years_since_law + outcome)

c_timing <- epreds_timing |> 
  filter(years_since_law %in% c(2017, 2022)) |> 
  group_by(years_since_law) |> 
  mutate(count = prop_to_provinces(.epred)) |> 
  median_qi(count) |> 
  mutate(across(c(.lower, .upper), list(whole = ~round(., 0)))) |> 
  mutate(count_median = round(count, 0)) |> 
  mutate(range = glue("{.lower_whole}–{.upper_whole}")) |> 
  mutate(years_since_law = make_clean_names(years_since_law)) |> 
  split(~ years_since_law)

c_timing_local <- epreds_timing_local |> 
  filter(years_since_law %in% c(2017, 2022)) |> 
  mutate(local_connect = case_match(local_connect, TRUE ~ "true", FALSE ~ "false")) |> 
  group_by(local_connect, years_since_law) |> 
  mutate(count = prop_to_provinces(.epred)) |> 
  median_qi(count) |> 
  mutate(across(c(.lower, .upper), list(whole = ~round(., 0)))) |> 
  mutate(count_median = round(count, 0)) |> 
  mutate(range = glue("{.lower_whole}–{.upper_whole}")) |> 
  mutate(years_since_law = make_clean_names(years_since_law, allow_dupes = TRUE)) |> 
  split(~ years_since_law + local_connect)
```

::: {.content-visible when-format="html"}
# Introduction {.hide}
:::

In the past two decades, nearly 100 countries have proposed or enacted legal measures designed to restrict nongovernmental organizations (NGOs) and civil society more broadly [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyRonPrakash:2016].[^ngo-clarification] According to the CIVICUS Civil Society Monitor, as of 2023 only `r civicus_prop$true$prop_nice` of countries have open and unrestricted civic space [@CIVICUSMonitor]. On April 28, 2016, China passed its own set of civil society restrictions with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China---or "2016 ONGO Law"---which formally took effect on January 1, 2017. The law requires all international NGOs (INGOs) to either establish formal in-country representative offices (ROs) or file short-term temporary activities to lawfully operate in mainland China. Without recognized legal status, INGOs are prohibited from working in the country, and even with legal recognition, INGO programming is limited to government-approved activities.

[^ngo-clarification]: "Civil society" is a broad concept that includes a range of organizational forms, both formal and informal. In this paper, we look at nonprofit organizations or third sector organizations---formal non-profit-seeking organizations that are neither privately-owned nor government-controlled. We define international NGOs as organizations that work predominantly in at least one other country outside of their home country.

As an authoritarian state with a growing nonprofit sector, China's regulatory regime for INGOs serves as an example for understanding how autocracies use restrictive laws as policy tools as they engage with international civil society. The policies implemented by China's 2016 ONGO law serve dueling purposes that both harness the benefits and reduce the risks of INGOs. The law is designed to decrease demand for foreign civil society organizations and limit the influence they might have over domestic policies [@DeMattee:2018; @DeMattee:2019] while also allowing the regime to benefit from the expertise, services, and reputational advantages of working partnering with international civil society [@Plantan:2022; @Heiss:2019]. These dual demands lead to differential enforcement and divergence between formal *de jure* regulations and the *de facto* implementation of those laws [@ChaudhryHeiss:2022], as the government enforces regulations selectively depending on regime preferences for INGO services.

In this paper, we use the case of China to explore how the demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2016 ONGO Law came into effect. We examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China, as well as the association between factors such as INGO issue areas and the operational space granted to them in the country. We contribute to a growing body of research on the effects of closing civic space on INGO behavior and strategies. First, we expand work that uses institutional approaches to understanding civil society regulations, which argues that states strategically regulate INGOs to maintain regime stability, choosing forms of regulation and repression that minimize threats to internal political stability [@Chaudhry:2022; @DeMattee:2018; @DeMattee:2019; @Heiss:2019]. Second, we explore how authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how these laws reshape and tame organizational strategies [@Li:2020; @LianMurdie:2023]. Third, we explore how these regulations lead to differentiated application of the law depending on organizational characteristics. We argue that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs.

By focusing on INGO operational space in China, we provide a unique empirical view into the *de facto* regulatory environment for foreign civil society in an authoritarian state. Broader indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the general regulatory environment for all civil society more broadly, but do not reflect the specific implementation of laws for INGOs. In this paper, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing a much richer description and analysis of the impact of INGO laws.

Below, we provide a brief overview of China's 2016 ONGO Law and the different regulatory mechanisms it provides for INGOs to obtain legal access to the country. We then synthesize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of theoretical expectations based on this literature. We test these expectations with a mixed methods research design, combining Bayesian analysis of administrative data from all `r nrow(ongo)` formally registered INGOs with a comparative case study of Greenpeace and The Nature Conservancy, two environmental INGOs that took different approaches to operating in China after 2017. We conclude with a broader discussion of authoritarian civil society regulations and propose future approaches for exploring the practical operating environment for INGOs working in such regimes.


# The legal framework established by the 2016 ONGO law

International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and global civil society has played pivotal roles in providing funding, organizational and program management skills, and catalytic support for China's emerging domestic nonprofit sector [@Yin:2009]. Before the 2016 ONGO Law, the regulation of INGOs in China was ambiguous [@Shieh:2018; @Spires:2022]. The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations, which required that foreign foundations register with the Ministry of Civil Affairs, the regulating agency for domestic nonprofits. However, the actual application of the regulation was very limited: fewer than 30 foreign foundations registered, compared to estimates of over 7,000 INGOs working in China in 2016 [@YeHuang:2018; @Spires:2020]. Many INGOs gained legal status by registering as foreign-invested companies [@Sidel:2016], allowing them to hire local employees [@HolbigLang:2022; @Yin:2009]. However, this legal form is not quite compatible with the non-profit-distributing, social service orientation of civil society [@Ye:2021]. INGOs registered as foreign-invested companies had to navigate incongruous for-profit regulations, such as rules protecting shareholders' investment returns.

The legal framework governing INGOs was overhauled by the 2016 ONGO Law, which applies to all overseas (including Hong Kong, Macau, and Taiwan) NGOs that conduct not-for-profit activities in mainland China. The ONGO Law provides two pathways for INGOs to lawfully operate in China (see @fig-ro-ta-pathways): (1) submitting an application for formal permanent registration as registered organizations, or (2) filing documentation of temporary activities with provincial Public Security Bureaus. Formal registration as an RO allows INGOs to maintain an ongoing presence in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year. Using one of these two channels to obtain legal status became mandatory in 2017. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.

```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Two possible pathways for international NGOs to legally work in 
#|   China under the 2016 ONGO law"

ro_nodes <- tibble(
  step = c(
    "Find a professional supervisory unit (PSU)",
    "Obtain PSU approval",
    "Open organization bank accounts",
    "Submit annual work plans to PSU and Public Security Bureau",
    "Keep programming within approved scope",
    "Submit annual reports to PSU and Public Security Bureau"
  ),
  type = "Representative offices"
)
ro_edges <- tibble(from = 1:5, to = 2:6)
ro_graph <- tbl_graph(nodes = ro_nodes, edges = ro_edges)

ta_nodes <- tibble(
  step = c(
    "Find an eligible Chinese partner to file paperwork",
    "File activity information with Public Security Bureau",
    "Keep programming within approved scope",
    "Finish work within a year",
    "Submit final project report to Public Security Bureau"
  ),
  type = "Temporary activities"
)
ta_edges <- tibble(from = 1:4, to = 2:5)
ta_graph <- tbl_graph(nodes = ta_nodes, edges = ta_edges)

combined_graph <- bind_graphs(ro_graph, ta_graph)

ggraph(combined_graph, layout = "tree") +
  geom_node_label(
    aes(x = x, y = y, label = step), 
    size = 2.5, label.r = unit(0, units = "pt")
  ) +
  geom_edge_link(
    aes(
      start_cap = label_rect(node1.step, padding = margin(5, 5, 5, 5, "pt")),
      end_cap = label_rect(node2.step, padding = margin(5, 5, 5, 5, "pt"))
    ),
    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
    edge_linewidth = 0.25
  ) +
  facet_nodes(vars(type), scales = "free_x") +
  labs(x = NULL, y = NULL) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
    strip.text = element_text(hjust = 0.5)
  )
```

Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental agency related to an INGO's issue area that oversees and co-supervises the INGO with provincial Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, as potential PSUs have no legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. INGOs vary in their ability to attract partner PSUs, and organizations that struggle to find suitable PSUs face limitations in their scope and geographic reach. After successfully gaining legal status, INGOs must follow the law's operational regulations, such as no fundraising within mainland China, only channeling funds through the RO's or PSU's bank accounts, filing reports regularly, and staying within the geographical and issue scopes as approved. INGOs undertaking temporary activities also need to find an eligible Chinese partner---including governmental, quasi-governmental, or non-profit organizations---and must keep their programs within approved limits, but the process is less onerous.

# Civil society laws in the service of regime stability

The 2016 ONGO Law's provision of two legal pathways for registration---each with different degrees of freedom---is an example of the broader phenomenon of closing civic space. In the past two decades, authoritarian states have used administrative and legal measures to curtail the influence of global civil society. A rich literature in comparative politics explores how authoritarian regimes counterintuitively use democratic institutions for their own benefit and survival [@Kendall-TaylorFrantz:2014a; @GandhiPrzeworski:2007]. Authoritarian states hold elections, allow opposition parties in the legislature, and set executive term limits [@Meng:2020], but use these democratic-appearing institutions to hedge against possible threats to regime stability. Quasi-democratic institutions are allowed, but only in ways that bolster the government's stability, and these institutions are kept weak and "dependent on the regime to ensure that they do not develop any real power or autonomy" [@FrantzEzrow:2011, 7].

Civil society is a democratic political institution that autocrats balance as part of their stability-seeking calculus. Despite the fact that NGOs can act as "agents of democratization" [@ToeplerZimmerFrohlich:2020], thus posing a threat to non-democratic rule, most authoritarian states permit the growth of domestic and international civil society [@DeMattee:2019; @Heiss:2019; @Heiss:2019a]. INGOs provide needed resources and expertise in humanitarian relief, education, and development, and autocrats can rely on these services to consolidate power by providing improved public goods. At the same time, INGOs can pose a threat to stability by exposing human rights abuses, encouraging unwanted political reform, and engaging in political advocacy [@Heiss:2019; @ToeplerZimmerFrohlich:2020]. To capture the benefits and reduce the risk of working with INGOs, most authoritarian states rely on "administrative crackdown" [@Chaudhry:2022], or laws that create barriers to NGO advocacy, entry, and funding [@ChristensenWeinstein:2013; @ChaudhryHeiss:2022; @CarothersBrechenmacher:2014]. These laws, however, are a blunt tool and target civil society as a whole---states do not create one set of formal laws that applies only to regime-friendly INGOs and another set that applies to riskier INGOs. Instead, there is a divergence between the formal *de jure* laws and the *de facto* implementation of their accompanying regulations. In practice, NGO laws tend to not be applied universally, and formal laws often serve as a "weapon hanging on the wall that never fires" [@Kozenko:2015], acting as a warning to potentially uncooperative NGOs. 

The authoritarian benefits of civil society regulations go beyond simply allowing or disallowing specific INGOs. Autocrats engage with INGOs in opposing ways, providing financial support and opportunities for collaboration with those that align with government policy preferences, and using legal mechanisms to restrict or expel those that do not [@ToeplerZimmerFrohlich:2020; @Plantan:2022; @LiFarid:2023]. The flexible *de facto* implementation of formal civil society laws allows authoritarians to "use nonprofit regulation as a tool of political control to shore up their continued rule" [@Spires:2020, 573], providing them with an additional policy tool for their stability-seeking calculus. These laws allow governments to capture and reshape INGO programming in their favor. Globally, increased civil society restrictions have counterintuitively led to an increase in cooperative, regime-friendly INGO programming, with INGOs praising government policies, engaging in joint programming with the government, and changing longstanding programs to align with government desires [@LianMurdie:2023].

China's ONGO law illustrates this dynamic well. The ONGO law requirement to partner with Public Security Bureaus and collaborate with PSUs provides the government with direct influence over INGO decision-making. For example, Oxfam gained RO status in 2017, but only after negotiations with its proposed PSU forced it to stop collaborating with other organizations and local agencies [@Li:2020]. In 2018, INGO programming showed signs of reorienting to be more explicitly aligned with government preferences [@BatkeHang:2018], and by 2021, the issue areas addressed by legally recognized INGOs had clearly "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [@HolbigLang:2022, p. 587]. Civil society laws thus filter out organizations opposed to the host regime's policy preferences and grant increased government control over safer and more beneficial INGOs.

# Authoritarian policy tools and INGO operational space: theory and expectations

The strategic and individualized enforcement of broad civil society laws in authoritarian regimes creates a regulatory environment where each INGO faces a different set of constraints. We term this an INGO's "operational space," or the degree of legal and practical flexibility an organization faces in its target country. INGOs with a large amount of operational space can engage in a wider range of programs, address more contentious issues, and enjoy broader geographic scope without fear of interference from the host government, even in the presence of formal *de jure* anti-NGO laws. Organizations with less operational space face stricter *de facto* regulatory environments and are more constrained in the programs, strategies, issues, and regions they can work on. 

```{r fig-theory, fig.width=6, fig.height=1.75}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Three proposed determinants of INGO operational space."
theory_nodes <- tribble(
  ~id, ~name, ~x, ~y, ~highlight,
  1,   "Issue contentiousness", 2, 1, FALSE,
  2,   "Operational space", 2, 0, TRUE,
  3,   "Local focus", 3, 1, FALSE,
  4,   "Government preferences", 1, 1, FALSE
)

theory_edges <- tribble(
  ~from, ~to,
  1, 2,
  3, 1,
  3, 2,
  1, 4,
  4, 1,
  4, 2
)

theory_graph <- tbl_graph(nodes = theory_nodes, edges = theory_edges, directed = TRUE)

ggraph(theory_graph, x = x, y = y) + 
  geom_edge_link(
    aes(
      start_cap = label_rect(node1.name, padding = margin(10, 0, 10, -05, "pt")),
      end_cap = label_rect(node2.name, padding = margin(10, -5, 10, -5, "pt"))
    ),
    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
    edge_linewidth = 0.25
  ) +
  geom_node_label(
    aes(x = x, y = y, label = name, fill = highlight), 
    size = 3, label.r = unit(0, units = "pt"), fontface = "bold"
  ) +
  scale_x_continuous(expand = expansion(add = 0.4)) +
  scale_y_continuous(expand = expansion(add = 0.2)) +
  scale_fill_manual(values = c("white", clrs[1]), guide = "none") +
  labs(x = NULL, y = NULL) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
  )
```

In @fig-theory, we propose that the interplay between INGO characteristics and government preferences is a key determinant of individual INGO operating space [@LiFarid:2023; @ChaudhryHeiss:2021]. Authoritarian states seek out INGOs that provide direct benefits, while avoiding INGOs that threaten their stability. For instance, states in need of foreign aid and development will be more open to INGOs working on those issues, while states looking for increased trade will seek out INGOs focused on economic partnerships. Because their primary issue areas are aligned with regime preferences, INGOs benefit from greater operational space and face fewer restrictions. In contrast, states engaged in human rights abuses or fearful of foreign influence over other domestic policies will reduce---or even close---the operational space allowed for INGOs addressing these issues. Notably, the arrow between government preferences and issue area is bidirectional, reflecting the government's ability to use civil society regulations to realign INGO programming in the regime's favor, and the INGO's potential ability to reshape government preferences [@Heiss:2019a]. Finally, the natural scope of an INGO's activities influences its allowed operational space outside of authoritarian stability-seeking calculus. Many INGOs purposely keep themselves small, non-confrontational, and non-political and limit themselves to work in only a small part of their target countries, having no plans to go beyond their hyperlocal scope. This naturally limits their operational space, but these limits are self-imposed and not directly related to government regulations.

To test the relationships between government preferences, INGO issue area, and INGO operational space, we apply this framework to China's ONGO law. Previous research has looked at the practical implementation of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society. By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal anti-INGO law has shaped the operational space for foreign organizations working in the country. Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the potential reach of INGOs and reshape their issue areas. We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs desire to engage in work in as broad a geographical scope as possible [@Li:2020]. For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service. Having the potential to shift programs to other provinces as needed thus provides a form of operational space. 

To structure our analysis, we propose a set of theoretical expectations based on @fig-theory. First, we expect that INGOs working on non-contentious, regime-aligned issues will have greater reach throughout the country:

> **E~1~**: Because they are seen as less of a threat to regime stability and more aligned with government policy preferences, INGOs working on less contentious issues should be registered in more provinces.

Using the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility and reach might not reflect reality. Some INGOs explicitly limit their operations to specific provinces, either because their programming is more tailored to local conditions, or because they do not feel a need to go through the longer process of obtaining national-level registration. Accordingly, we temper our issue area expectation with a measure of explicitly local purpose. Organizations that have no intention of registering nationally should be registered in fewer provinces:

> **E~2~**: Because they are explicitly focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.

Finally, we also expect that the operational space for INGOs is negatively associated with the time elapsed since the law took effect. The mechanism behind this expectation is directly related to both issue area and government preferences:

> **E~3~**: Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces.


# Data and methods

We examine these theoretical expectations using a mixed methods approach. First, we explore a rich dataset of all ROs registered in China between 2017–2021 using Bayesian regression models to understand how the international civil society in China has been reshaped since the implementation of the ONGO law. We then complement this statistical analysis with a comparative case study of two INGOs---The Nature Conservancy and Greenpeace---to explore in detail how the ONGO has specifically influenced organizational operational space.

## Data

Our data comes from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office, which maintains a website with complete documentation of all the ROs and temporary activities registered or filled across China. We include all INGO registrations between January 1, 2017, when the law took effect, to December 31, 2021, with information for all `r nrow(ongo)` actively registered organizations. The filing documents for ROs disclose each INGO's name, address, registration date, regulating Public Security Bureau, PSU, issue area and purposes of the RO, and the specific provinces they can work in. We merge this INGO data with translated English organization names from ChinaFile. Our data and reproducible code are available at `ANONYMIZED_DOI_URL`.

Our dependent variable is the count of provinces that INGOs are authorized to work in. We derive this value from the official registration record, which lists all the provincial regions each INGO RO can conduct activities in. This value ranges from 1–32, the total number of province-level jurisdictions in mainland China. There are clear geographic trends in this measure. @fig-home-office-map shows that Beijing (`r provinces$beijing$ro_count`), Shanghai (`r provinces$shanghai$ro_count`), and Guangdong Province (`r provinces$guangdong$ro_count`) host the most ROs, while other provinces have as many as `r province4th[[1]]$ro_count` and as few as 1 permitted RO.

```{r fig-home-office-map}
#| include: true
#| echo: false
#| fig-cap: "Count of registered organizations across provinces"
# Extract the intersections of provinces so that we don't plot the outside
# borders and distort the coastlines. See https://stackoverflow.com/a/57138069 
# and https://ikashnitsky.phd/2023/map-borders/
interior_borders <- st_intersection(ongo_mapdata) |>
  filter(n.overlaps > 1) |> 
  # Remove weird points that st_intersection() adds
  filter(!(st_geometry_type(geometry) %in% c("POINT", "MULTIPOINT")))

# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
ggplot() +
  geom_sf(data = ongo_mapdata, aes(fill = ro_count), color = NA) +
  geom_sf(data = interior_borders, linewidth = 0.3, color = "white") +
  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none", na.value = "gray80") +
  geom_label_repel(
    data = filter(ongo_mapdata, ro_count > 0),
    aes(label = ro_count, geometry = geometry),
    stat = "sf_coordinates", seed = 1234, label.size = 0.05, size = 3,
    color = "black", fill = scales::alpha("white", 0.7),
    segment.color = "black", segment.size = 0.25, min.segment.length = 0
  ) +
  coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000
  theme_void()
```

Our key independent variables correspond to each of our three theoretical expectations. First, we code each INGO's issue area based on its mission statement reported in its registration documentation. Given the subjectivity in the coding process, we cross-checked our manual coding of issue areas (see the appendix for a description of our coding). We categorize each organization into nine different issue areas (see @tbl-issues). @fig-issue-props shows the distribution of these issue areas. The two most common issues are economic, trade, and industry associations, representing `r label_percent()((issues$industry_association$n + issues$economy_and_trade$n) / sum(issue_count$n))` (`r issues$industry_association$n + issues$economy_and_trade$n`) of all INGOs. Many of these organizations are bilateral chambers of commerce or other multilateral trade organizations. Charitable, humanitarian, education, and health INGOs are far less common than their trade and industry counterparts: charity and humanitarian organizations comprise `r issues$charity_and_humanitarian$prop_nice` (`r issues$charity_and_humanitarian$n`) of ROs.

::: {#tbl-issues}

```{r}
#| label: table-issues
#| include: true
tribble(
  ~Issue, ~Examples,
  "Arts and culture", "World Dance Council; Special Olympics",
  "Charity and humanitarian", "Save the Children; World Vision",
  "Economy and trade", "World Economic Forum; Canada China Business Council",
  "Education", "Children’s Education Foundation; BSK International",
  "Environment", "The Nature Conservancy; World Wide Fund for Nature",
  "General", "Bill and Melinda Gates Foundation; Ford Foundation",
  "Health", "American Heart Association; Operation Smile",
  "Industry association", "World Cement Association; Colombian Coffee Growers Federation",
  "Science and technology", "Royal Aeronautical Society; American Society of Civil Engineers"
) |> 
  gt() |> 
  tab_footnote(
    footnote = "Includes poverty alleviation, disaster relief, rural development, etc.",
    locations = cells_body(columns = Issue, rows = 2)
  ) |> 
  tab_footnote(
    footnote = "Includes grant-making organizations, organizations working on general international communication, and organizations working on multiple non-overlapping issues",
    locations = cells_body(columns = Issue, rows = 6)
  ) |> 
  cols_width(Issue ~ gt_pct(20), Examples ~ gt_pct(50)) |> 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) |>
  opts_theme() |> 
  tab_options(
    quarto.disable_processing = TRUE
  )
```

Possible INGO issue areas and example organizations

:::

```{r fig-issue-props, fig.width=6, fig.height=3}
#| include: true
#| echo: false
#| fig-cap: "Count of international NGO registrations, divided by issue area"

ggplot(issue_count, aes(y = work_field_code1, x = n)) +
  geom_col(fill = clrs[5]) +
  scale_x_continuous(sec.axis = sec_axis(trans = ~ . / sum(issue_count$n),
                                         labels = label_percent())) +
  labs(x = "Count of INGOs", y = NULL) +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

Our second independent variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally or sub-provincially. There are cases where the aim of the INGO is attached to a locality, either having a county or city name in their RO name or purposes, or the INGO is actually set up by people in China who registered the RO to communicate between the "hometown" and the INGO set up abroad. Of the `r nrow(ongo)` ROs, `r loc$true$n` (`r loc$true$prop_nice`) have a narrow local focus.

Our final independent variable measures how much time elapsed between January 1, 2017 and the organization's official registration date. There is great variance in registration timing, since there was a brief grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018]. Nearly half of all ROs---`r ros_2017$prop_nice`---registered in 2017, and the count of new registrations gradually declined after the initial first-year wave (see @fig-registration-timeline). This is largely because both INGOs and the regulators needed some transitional time to explore the specific application of the law as large ambiguity was left when the law was passed. We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register as an RO, since INGOs may have been inclined to avoid the cumbersome registration procedures at the early stage if there were no real consequences for delaying, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic [@Jia:2017a].

```{r fig-registration-timeline, fig.width=6, fig.height=3}
#| include: true
#| echo: false
#| fig-cap: "Count of international NGO registrations under the 2016 ONGO Law, 
#|   divided by quarters"

ggplot(ongo, aes(x = registration_date)) +
  geom_histogram(binwidth = 365.25/4, boundary = ymd("2017-01-01"), 
                 fill = clrs[6], color = "white") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  labs(x = NULL, y = "Count of new INGO registrations") +
  theme_ongo()
```

## Modeling approach

We use a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility. This approach allows us to hold specific variables constant and generate predictions for hypothetical new, not-yet-registered INGOs, providing us with stronger empirical implications. Additionally, Bayesian modeling allows us to analyze the uncertainty associated with INGO operational space---instead of reporting a single value for the number of provinces INGOs have access to, we report posterior credible intervals that represent the probability that the average geographic reach falls within a specific range.

```{r fig-province-count-collapsed, fig.width=6, fig.height=3}
#| include: true
#| echo: false
#| fig-cap: "Count of the number of provinces each INGO is authorized to operate 
#|   in. The left panel shows the full distribution of INGOs registered in 2–31 
#|   provinces; the right panel collapses these in-between counts into to a 
#|   single category."

provinces_collapsed <- ongo |> 
  drop_na(province_count) |> 
  mutate(province_count = case_when(
    province_count == 1 ~ "1",
    province_count > 1 & province_count < 32 ~ "2–31",
    province_count == 32 ~ "32"
  ))

p1 <- ggplot(ongo, aes(x = province_count)) +
  geom_histogram(binwidth = 1, linewidth = 0.1, boundary = 0,
                 fill = clrs[6], color = "white") +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  labs(x = "Provinces INGOs are authorized to work in", y = "Count") +
  theme_ongo()

p2 <- ggplot(provinces_collapsed, aes(x = province_count)) + 
  geom_bar(fill = clrs[6]) +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(sec.axis = sec_axis(trans = ~ . / nrow(provinces_collapsed),
                                         labels = label_percent()),
                     breaks = seq(0, 250, 50)) +
  labs(x = NULL, y = NULL) +
  theme_ongo()

(p1 | p2) + 
  plot_layout(nrow = 1, widths = c(0.7, 0.3))
```

Modeling the count of provinces each INGO is authorized to operate in presents a unique statistical challenge. As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2--31 provinces. Our main variable of interest is thus a mix of continuous outcomes (i.e. a range of provinces) bounded between two discrete outcomes (i.e. one province and all provinces). Standard modeling approaches like ordinary least squares regression (OLS) cannot accurately capture the unique features of the data and will generate predictions that fall outside allowable bounds (i.e. negative counts of provinces or more than 32 provinces). To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2--31) and the discrete outcomes (1 province and 32 provinces). We can thus explore the dynamics of each of our independent variables of interest in multiple ways---we can see how each variable (1) predicts that an organization works in one province, nationwide, or somewhere in between, and (2) predicts the overall expected count of provinces. 

Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables. We also include random province intercepts to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus. We use the following model and priors; additional model details and results are available in the appendix and in TABLE TODO:

$$
\begin{aligned}
&\ \textbf{Registered provinces for INGO } i \\
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
&\ \textbf{Model of outcome average} \\
\mu_i =&\ 
  \mathrlap{\begin{aligned}[t]
  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
  \end{aligned}}\\[8pt]
&\ \textbf{Priors} \\
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
\end{aligned}
$$


# Results and discussion

## Model results

### Issue area

Next, we explore the data in more depth by generating and analyzing posterior predictions from our model. Following our first theoretical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and thus have more geographic flexibility. We take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between. @fig-issue-preds(a) presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each issue area and holding all other variables at their mean or modal values. 

Several notable trends emerge from the model results. INGOs focused on arts and culture are overwhelming the most likely kind of organization to work nationally---arts and culture organizations are predicted to work in all 32 provinces `r p_issue$arts_and_culture.all_32_provinces$prop_ci_nice` of the time and are only predicted to work in a single province a rare `r p_issue$arts_and_culture.only_1_province$prop_ci_nice` of the time. Education-focused INGOs, on the other hand, are the least likely kind of organization to be registered in all 32 provinces and are predicted to do so only `r p_issue$education.all_32_provinces$prop_ci_nice` of the time. Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing `r p_issue$education.only_1_province$prop_ci_nice` of the time---15--20 percentage points higher than any other issue area's predicted proportion. All other issue areas follow roughly similar patterns in predictions: the most common outcome is for organizations to work nationally (≈45--60% of the time), followed by working in at least 2 provinces (≈25--35% of the time), followed by working in a single province (≈15--30% of the time). @fig-issue-preds(b) shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously. We can see a similar trend---arts and culture INGOs are predicted to work in `r c_issue$arts_and_culture$range` provinces on average, while education INGOs are only predicted to work in `r c_issue$education$range`. All other issues range between 15--25 provinces.

```{r fig-issue-preds, fig.width=8, fig.height=6.5}
#| include: true
#| echo: false
#| column: body-outset
#| fig-cap: "Posterior predictions conditional on organization issue area. 
#|   **A**: Predicted proportion of INGOs working in 1 province, all 32 
#|   provinces, or somewhere in between. 
#|   **B**: Expectation of posterior predictive distributions."

p1 <- preds_issue_plot |>
  mutate(issue_area_nice = factor(
    issue_area_nice,
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  )) |>
  ggplot(aes(x = draw, y = prop)) +
  geom_area(
    aes(fill = outcome, color = after_scale(fill)),
    position = position_stack(), linewidth = 0.1
  ) +
  geom_text(
    data = preds_issue_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
  labs(
    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
    title = "Predicted proportion of type of geographic reach across issue area",
    subtitle = "Posterior predictions of outcome categories",
    tag = "A",
    caption = str_wrap(
      glue(
        "The vertical slices of the bars depict 500 posterior samples;",
        "the fuzziness represents the uncertainty in category boundaries.",
        "95% credible intervals are shown as ranges in each category",
        .sep = " "
      ),
      width = 120
    )
  ) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

p2 <- epreds_issue |>
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |>
  mutate(issue_area_nice = factor(
    issue_area_nice,
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  )) |>
  ggplot(aes(x = issue_area_nice, y = prop_to_provinces(.epred))) +
  stat_halfeye(fill = clrs[6], color = clrs[8]) +
  scale_x_discrete(labels = NULL) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1, scales = "free_x") +
  guides(fill = "none") +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces",
    subtitle = "Expectation (or average) of posterior predictions",
    tag = "B",
    caption = str_wrap(
      glue(
        "These distributions take into account single-province and nationwide predictions",
        "and represent the overall conditional average geographic range for INGOs.",
        "Points show posterior median; lines show 80% and 95% credible intervals.",
        .sep = " "
      ),
      width = 120
    )
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  theme_ongo() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

p1 / p2
```

As explained previously, we expect that the contentiousness of an NGO's issue area should influence its geographic reach and overall flexibility. No INGOs engaged in contentious issues like human rights advocacy have successfully registered in China, but there is some slight variation in the level of contention even among organizations working on less contentious issues like humanitarian assistance, health, and the environment. Education is particularly notable as the least flexible and most geographically restricted subsector. While education is typically considered a low-contention issue, in China fears of Western influence through educational institutions were an original impetus for the ONGO law. In 2006, an article in a CCP-owned newspaper warned that the growing presence of international NGOs would "undermine national security," "destroy political stability," "foster corruption," "propagate foreign practices," and "spy on and gather information on China's military, political, and economic information" [@Yin:2009, 534]. The idea that INGOs would "propagate foreign practices" had especially powerful salience, since increased exposure to the West through international NGOs had the potential to "lead to adoption of Western ideas of liberty, further endangering government control over the populace" [@HsiaWhite:2002, 337]. Educational NGOs were one particular avenue for the West to exert influence in the country---the directors and presidents of dozens of China's largest domestic NGOs have received doctoral degrees from and hold visiting appointments at Cornell, Duke, UNC-Chapel Hill, Harvard, Yale, and other prominent US universities [@Wang:2012, 108--9], and their training and connections abroad have influenced their programming and advocacy at home. In 2006, one Chinese NGO leader candidly explained that "foreign influence is definitely great. There is conceptual influence. Foreign NGOs' working methods also affect Chinese NGOs" [@Wang:2012, 110]. Education is therefore one of the more contentious issues allowed under the ONGO law, and thus more closely regulated and restricted.

### Local connections

In our second theoretical expectation, we posit that since INGOs that seek out local connections and that are focused on more local China-specific issues, those organizations should be registered in fewer provinces. The results from our model confirm this expectation. @fig-local-preds(a) shows that organizations without local connections are predicted to work nationally across all provinces nearly half of the time (with a 95% credible interval of `r p_loc$no_local_connections.all_32_provinces$prop_ci_nice`), with a `r p_loc$no_local_connections.between_1_32_provinces$prop_ci_nice` probability of working in two or more provinces. INGOs without local connections only have a `r p_loc$no_local_connections.only_1_province$prop_ci_nice` probability of working in a single province. In contrast, INGOs with local connections are far more likely to only work in one province (`r p_loc$local_connections.only_1_province$prop_ci_nice`), or only work in a handful of provinces (`r p_loc$local_connections.between_1_32_provinces$prop_ci_nice`). For these locally-focused organizations, the least common prediction is to work nationally, with only a `r p_loc$local_connections.all_32_provinces$prop_ci_nice` probability. @fig-local-preds(b) shows the posterior distribution of the average number of provinces INGOs are expected to be registered in, conditional on their local connections. The same relationship holds---an INGO without local connections is predicted to work in `r c_local$false$range` provinces on average, while an organization with local connections is only predicted to work in `r c_local$true$range`.

```{r fig-local-preds, fig.width=8, fig.height=4.5}
#| include: true
#| echo: false
#| fig-cap: "Posterior predictions conditional on having local connections. 
#|   **A**: Predicted proportion of INGOs working in 1 province, all 32 
#|   provinces, or somewhere in between. 
#|   **B**: Expectation of posterior predictive distributions."

p1 <- preds_local_plot |> 
  ggplot(aes(x = draw, y = prop)) +
  geom_area(
    aes(fill = outcome, color = after_scale(fill)), 
    position = position_stack(), linewidth = 0.1
  ) +
  geom_text(
    data = preds_local_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1) +
  labs(
    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
    title = "Predicted proportion of type of\ngeographic reach across local connections",
    subtitle = "Posterior predictions of outcome categories",
    tag = "A",
    caption = str_wrap(
      glue(
        "The vertical slices of the bars depict 500 posterior samples;",
        "the fuzziness represents the uncertainty in category boundaries.",
        "95% credible intervals are shown as ranges in each category",
        .sep = " "
      ),
      width = 80
    )
  ) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

p2 <- epreds_local |>
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
  ggplot(aes(x = local_connect, y = prop_to_provinces(.epred))) +
  stat_halfeye(fill = clrs[6], color = clrs[8]) +
  scale_x_discrete(labels = NULL) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1, scales = "free_x") +
  guides(fill = "none") +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces",
    subtitle = "Expectation (or average) of posterior predictions",
    tag = "B",
    caption = str_wrap(
      glue(
        "These distributions take into account single-province and nationwide predictions",
        "and represent the overall conditional average geographic range for INGOs.",
        "Points show posterior median; lines show 80% and 95% credible intervals.",
        .sep = " "
      ),
      width = 50
    )
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  theme_ongo() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

(p1 | p2) +
  plot_layout(widths = c(0.63, 0.37), guides = "collect")
```

INGOs with locally focused missions and connections with provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader missions have a larger geographic reach. While we cannot precisely tell which direction the causal story works with this phenomenon, we can make some reasonable speculations. It is likely that locally-oriented INGOs purposely network and seek out connections with local PSUs before formally registering, thus fostering better relationships with government officials and furthering the organization's mission within its limited provinces. It is also likely, given the high probability of national reach, that organizations without local connections purposely do not spend the time and effort to cultivate those relationships, as it is not necessary to operate across many provinces. A rival explanation that having local connections reduces an organization's operational space does not seem warranted—although INGOs with local connections do have a more limited geographic scope, organizations appear to purposely limit the number of provinces they work in in order to focus more on their local work.

### Registration timing

In our third theoretical expectation, we propose that early registrants were both less of a threat to regime stability and a higher priority for bureaucratic processing and thus should be registered in more provinces. However, the results of our model support the opposite of this expectation. In @fig-timing-preds(a) organizations that registered in the first year have a `r p_timing$x2017.all_32_provinces$prop_ci_nice` probability of working in all provinces and are predicted to work in two or more provinces `r p_timing$x2017.between_1_32_provinces$prop_ci_nice` of the time. These early INGOs are the most likely to be registered in only one province and are predicted to do so `r p_timing$x2017.only_1_province$prop_ci_nice` of the time. After 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces. By the end of 2021 the probability of national-level registration increases to `r p_timing$x2022.all_32_provinces$prop_ci_nice` while the probability of working in a range of provinces increases to predicted to work in two or more provinces remains around `r p_timing$x2022.between_1_32_provinces$prop_ci_nice`. These later INGOs are the least likely to be registered in only one province, with a probability of `r p_timing$x2022.only_1_province$prop_ci_nice`. @fig-timing-preds(b) demonstrates the expected count of provinces over five years since 2017. INGOs that register early are predicted to work in `r c_timing$x2017$range` provinces on average, while those that wait until 2021 are predicted to work in a far more uncertain `r c_timing$x2022$range`.

```{r fig-timing-preds, fig.width=8, fig.height=4.5}
#| include: true
#| echo: false
#| fig-cap: "Posterior predictions conditional on time since law took effect. 
#|   **A**: Predicted proportion of INGOs working in 1 province, all 32 
#|   provinces, or somewhere in between. 
#|   **B**: Expectation of posterior predictive distributions."

preds_timing_text <- preds_timing_plot |> 
  filter(years_since_law == 2017.2) |> 
  group_by(outcome) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
  mutate(y_plot = 1 - y_plot) |> 
  mutate(years_since_law = 2017.2)

layers <- preds_timing_plot |> 
  filter(draw <= 50) |> 
  split(~ draw) |> 
  lapply(\(x) {
    geom_area(
      data = x,
      aes(y = prop, fill = outcome),
      alpha = 0.1
    )
  })

p1 <- ggplot(preds_timing_plot, aes(x = years_since_law)) +
  layers +
  geom_text(
    data = preds_timing_text, 
    aes(y = y_plot, label = outcome),
    color = "white",
    hjust = 0, fontface = "bold", size = 3, show.legend = FALSE
  ) +
  scale_x_continuous(expand = expansion(mult = 0.02)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_color_manual(values = colorspace::darken(clrs[c(3, 5, 7)], 0.1)) +
  scale_fill_manual(values = colorspace::lighten(clrs[c(3, 5, 7)], 0)) +
  labs(
    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
    title = "Predicted proportion of type of \ngeographic reach since January 2017",
    subtitle = "Posterior predictions of outcome categories",
    tag = "A",
    caption = str_wrap(
      glue(
        "Filled areas depict 50 posterior samples of the outcome category probabilities;",
        "the fuzziness represents the uncertainty in category boundaries; ",
        .sep = " "
      ),
      width = 60
    )
  ) +
  guides(fill = "none") +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank()
  )

p2 <- epreds_timing |>
  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
  stat_lineribbon(
    .width = c(0.5, 0.8, 0.95),
    alpha = 0.35, fill = clrs[6], color = clrs[6]
  ) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces",
    subtitle = "Expectation (or average) of posterior predictions",
    tag = "B",
    caption = str_wrap(
      glue(
        "This distribution takes into account single-province and nationwide",
        "predictions and represents the overall conditional average geographic",
        "range for INGOs over time.",
        "Shaded regions show the 50%, 80%, and 95% credible intervals.",
        .sep = " "
      ),
      width = 65
    )
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  theme_ongo()

p1 | p2
```

We lack sufficient theory to explain why this trend goes against our expectations, but we can again make reasonable speculations. As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues for registering [@Jia:2017a]. Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily. As a preliminary test of this speculation, we rerun our main model with an interaction between years since registration and local connections to see how the effect of local connections changes over time. As seen in @fig-timing-local, early registrants in 2017 without local connections are more likely to have a larger geographic reach, registering in an average of `r c_timing_local$x2017.false$range` provinces, while their locally-focused counterparts are only expected to register in an average of `r c_timing_local$x2017.true$range` provinces. Accordingly, it may be that INGOs with local connections are more likely to register early because of their pre-existing bureaucratic relationships, while organizations with a larger national reach take longer to undertake the registration process and thus register later. Another possible explanation could be that earlier registration signals greater eagerness to reduce the uncertainty surrounding organizational legal status. INGOs that perceive themselves as more contentious may be more nervous about the legal consequences of not being able to register and thus be more willing to seek registration earlier [@ChinaPhilanthropyReserchInstitute:2018]. Compared with their safer, less contentious peers, INGOs seeking to register earlier are more likely to have reduced operational space. To understand the underlying mechanism with registration timing, further research is warranted.

```{r fig-timing-local, fig.width=6, fig.height=3.4, out.width="80%"}
#| include: true
#| echo: false
#| fig-cap: "Expectation of posterior predictive distributions from model with 
#|   interaction between local connections and time since January 2017."

epreds_timing_local |>
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
  stat_lineribbon(
    .width = c(0.5, 0.8, 0.95),
    alpha = 0.35, fill = clrs[6], color = clrs[6]
  ) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  guides(fill = "none") +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces across local connections",
    subtitle = "Expectation of posterior predictions",
    caption = str_wrap(
      glue(
        "These distributions take into account single-province and nationwide",
        "predictions and represents the overall conditional average geographic",
        "range for INGOs over time.",
        "Shaded regions show the 50%, 80%, and 95% credible intervals.",
        .sep = " "
      ),
      width = 90
    )
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  facet_wrap(vars(local_connect)) +
  theme_ongo()
```

## Contentiousness and government relationships: The cases of The Nature Conservancy and Greenpeace 

The results from our model provide useful insight into the operational space of INGOs that have been able to formally register. These organizations have been pre-screened and deemed to be safe and non-contentious. This can help explain why some seemingly more contentious issue areas such as environmental INGOs enjoy relatively more operational space (see @fig-issue-preds). Chinese authorities can benefit politically from the of environmental INGOs and "selectively encourage low risk groups and selectively channel higher risk groups into permitted areas" [@Plantan:2022, 504]. Using our data, however, we are unable to make comparisons with already-vetted INGOs and other potentially more contentious organizations, which limits our analysis of the determinants of operational space. To address this, we compare the cases of two environmental INGOs: (1) The Nature Conservancy (TNC), which successfully registered as RO under the ONGO Law, and (2) Greenpeace, which has filed dozens of sequential temporary activities.

TNC and Greenpeace are both well-known environmental INGOs. Both are based in Western countries and have offices around the world. They each began working in China around the turn of the century, with TNC in establishing an office in Beijing in 1998 and Greenpeace in 2001. Despite these similarities, the two INGOs have had quite different experiences to sustain their legal presence in China after the ONGO Law took effect. TNC obtained RO status in May 2017, partnering with the National Forestry and Grassland Administration as their PSU, and receiving authorization to work in 27 provinces. In contrast, Greenpeace has not received RO status and has instead filed 67 temporary activities, filing new documentation nearly ten times each year. 

Essentially, constantly filing temporary activities has become a circumvent for INGOs like Greenpeace to maintain long-term presence in China [@Corsetti:2019]. However, choosing a legal channel mostly meant for one-off programs results in far more limited INGO operational space than under RO regulations (recall @fig-ro-ta-pathways). Securing a new partnership with a Chinese organization for each activity and co-filing the requisite paperwork imposes substantial administrative costs. This approach also creates high uncertainty, since there is no guarantee that a current partner organization would agree to repeat their role for the next project. Moreover, INGO programming has an inherent short-term focus, given that temporary activities cannot last longer than a year. Finally, temporary activities need to focus on safe activities with few political risks in order to attract potential Chinese partners. 

One key difference in these two organizations' differing registration strategies is their relationship with the government and alignment with government preferences. TNC has stated that its work "science-based" and that the organization uses a "non-confrontational, collaborative approach in working closely with governments, the business community and others. [@ChinaPhilanthropyReserchInstitute:2018a] Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030)[@todo]<https://www.nature.org/en-us/about-us/where-we-work/asia-pacific/china/stories-in-china/china-overview/>. This deliberately non-confrontational model, coupled with long-established partnerships with the government enabled TNC to secure the consent of a environment-focused national governmental agency to act as their PSU, which in turn allowed TNC to have a wider geographic reach throughout the country. Moreover, TNC's work with local and national governments has generally been aligned with government preferences and directly benefits the regime. 

In contrast, Greenpeace engages in direct advocacy, "us[ing] peaceful protest and creative confrontation to expose global environmental problems" [@todo]<https://www.greenpeace.org/usa/about/>. The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change", indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@todo]<https://www.greenpeace.org.cn/about/mission-and-value/>. In 2004, for instance, Greenpeace conducted three rounds of independent investigations into damages caused by the Sinar Mas Group, revealing how the Asian multinational corporation used promises of reforestation work as a cover while logging natural forests in Yunnan [@todo]<https://www.greenpeace.org.cn/2022/11/18/%e4%ba%a4%e9%94%8b%e4%ba%9a%e6%b4%b2%e6%9c%80%e5%a4%a7%e9%80%a0%e7%ba%b8%e5%b7%a8%e9%b3%84%ef%bc%8c%e5%ae%88%e6%8a%a4%e4%ba%91%e5%8d%97%e5%a4%a9%e7%84%b6%e6%9e%97-%e7%bb%bf%e8%89%b2%e5%92%8c/>. Greenpeace's ongoing independent advocacy work is often at odds with regime preferences, and from the government's perspective, its Chinese programming is unpredictable and less directly manageable. As a result, few potential PSUs have shown interest in sponsoring any potential registration attempt, and Greenpeace has chosen to not try to permanently register and instead work through repeated temporary activities.

@tbl-case-study summarizes the cases of TNC and Greenpeace. In addition to confirming the correlation between issue area and operational space found in the statistical model, the cases highlight how government preferences exert influence on both the degree of contentious programming INGOs are allowed to undertake and the severity of legal restrictions INGOs can face.

::: {#tbl-case-study}

```{r}
#| label: table-case-study
#| include: true

compare_table <- read_csv(here::here("data", "manual_data", "table-case-study.csv"))

compare_table |> 
  gt(rowname_col = "Characteristic") |> 
  cols_width(Characteristic ~ gt_pct(20), everything() ~ gt_pct(30)) |>
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) |>
  tab_style(
    style = cell_text(v_align = "top", weight = "bold"),
    locations = cells_stub()
  ) |>
  opts_theme() |> 
  tab_options(
    quarto.disable_processing = TRUE
  )
```

Comparison of the work of The Nature Conservancy and Greenpeace in China

:::


# Conclusion

Political institutions are central to authoritarian stability as autocrats work to co-opt and balance institutional challenges to their regime. Autocrats treat civil society---both domestic and international---as yet another actor in their stability-seeking calculus. The ongoing phenomenon of closing civic space, where governments worldwide continue to impose repressive regulations on civil society, can be seen as a strategy for stabilizing authoritarian rule [@DeMattee:2019; @CarothersBrechenmacher:2014; @Heiss:2019]. Notably, these laws are not enforced universally or consistently. The strategic enforcement of civil society laws creates a divergence between formal *de jure* regulations and the *de facto* implementation of those laws. Formal laws provide a legal framework for regulating INGOs, but government flexibility in enforcing those laws allows regimes to (1) act leniently towards organizations that offer services and expertise that benefit the regime, and (2) restrict, repress, or expel organizations that are deemed a risk to regime stability. 

We argue that regime preferences interact with organizations' issue areas to create variation in INGO operational space, or the *de facto* regulatory environment afforded to INGOs. We explore this theory by analyzing a novel dataset of all INGOs that have successfully registered in China since the implementation of the 2016 ONGO Law, a legal mechanism that provided the government with the ability to grow and shrink INGO operational space in strategic ways. By focusing on a specific law in one country, our work provides rich empirical illustrations of the mechanics of authoritarian administrative crackdown. We find that INGOs that work on issues that are less threatening and more aligned with regime preferences---such as arts & culture INGOs, industry associations, and scientific organizations—are registered in more provinces and thus enjoy a greater degree of operational space, while organizations that pose a potential threat---like education INGOs---are far more limited geographically. Our case study finds similar results. Because of its less confrontational approach and its connections to local government officials, The Nature Conservancy was able to obtain RO status and benefit from increased operational space while the more advocacy-focused Greenpeace has resorted to filing dozens of program-specific temporary activities.

Studying INGOs in authoritarian regimes poses a number of limitations, but the concept of operational space can address some of these issues in the future. First, we can only observe organizations that successfully registered as ROs. We cannot make comparisons with INGOs that left the country prior to 2017 or INGOs that have explicitly chosen to not work in China. This is not an issue specific to China---analyzing the international nonprofit sector of any country that has passed similar laws will raise similar issues of selection bias. The Chinese context provides one possible way forward: future research can further explore relationship between INGOs and regime preferences by comparing characteristics of INGOs that register as ROs or undertake temporary activities using already-available administrative data. Second, this paper focuses exclusively on INGO regulations in China, and the specific legal mechanisms for controlling INGOs in other countries will naturally differ. However, the findings are still instructive. We have illustrated how the implementation of one INGO law has reshaped the role of international civil society, leading to a preponderance of regime-friendly NGOs, many of which have realigned their programming with government preferences. It is likely that a similar dynamic plays out in other countries---regimes legislate civil society broadly and enforce those laws specifically. Future research might analyze the determinants of INGO operational space in other authoritarian states, which can help INGOs facing legal crackdown abroad strengthen their organizational flexibility in the face of legal restrictions.


# References

::: {#refs .bibliography}
:::
