---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
date: "2023-04-07"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
abstract: |
  China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international NGOs (INGOs). However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws. Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations. In this paper, we measure the effect of China’s ONGO law on INGO operations in the five years since the passage of the law. We test whether and how INGO operational space under the ONGO law is influenced by organizations’ issue areas. We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by thenumber of provinces they are allowed to work in by the registration documentation. China provides an excellent setting for testing the "closing space" and "changing space" theoretical understanding because the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities. We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with multilevel Bayesian models. Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
keywords:
  - international NGOs
  - civil society
  - authoritarianism
  - Chinese ONGO law
bibliography: references.bib
link-citations: true
---

```{r setup, include=FALSE}
if (is.null(knitr::pandoc_to())) {
  fmt_out <- "interactive"
} else {
  fmt_out <- knitr::pandoc_to()
}

knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
                      warning = FALSE, message = FALSE)

knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                      fig.width = 6, fig.height = (6 * 0.618),
                      out.width = "80%", collapse = TRUE)

options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r libraries-data}
library(tidyverse)
library(scales)
library(lubridate)
library(tidybayes)
library(marginaleffects)
library(patchwork)
library(kableExtra)
library(gt)
library(targets)

tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

# Generated via random.org
set.seed(8511)

# Load targets 
tar_load(ongo)
tar_load(ongo_mapdata)
tar_load(c(preds_issue, preds_local, preds_timing,
           epreds_issue, epreds_local, epreds_timing))

# Plotting and modelsummary functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))

prop_to_provinces <- function(x, lower = 1, upper = 32) {
  (x * (upper - lower)) + lower
}
```



# Introduction 

In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020; @ChaudhryHeiss:2020; @Heiss:2017; @Sidel:2023; AtiaHerrold:2018] (*to update citation*). An ubiquitous manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022a]. China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a recent global wave of legal restrictions on INGOs. As an authoritarian jurisdiction with a growing nonprofit sector, the Chinese model of implementing restrictive laws for INGOs has great implications for scholarly understanding of the dynamics of how such laws are used as policy tools to harness INGOs in practice. The purpose of this study is to empirically examine how the ONGO Law has impacted INGO's presence as well as the operational space after the law took effect. By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we intent to inquire into a more comprehensive and data-based picture of the operational space for INGOs. It will also test out the evolving theory of the "closing space" or "changing space" for INGOs hold true in a representative empirical setting of the mainland China. 


INGOs came to China after the Reform and Opening-up policy was adopted by the authority and have been playing pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector [@Yin:2009]. Before the promulgation of the ONGO Law, the regulation of INGOs in China was obscure [Shieh:2018; Spires:2022]. The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices (“ROs”) of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs. However, the actual application of the regulation was very limited. Up until the ONGO Law took effect on January 1, 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs according to the Regulation on the Management of Foundations, while some Chinese officials estimated in 2016 that there were roughly over 7000 ONGOs operating in China [@YeHuang:2018]. 

Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011]. They choose to have a formal legal identity for the convenience such as signing labor contracts directly with employees. However, the legal form of foreign-funded company is not quite compatible with the nature of ONGOs. Under the Chinese legal system, enterprises should be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms for them — foundations, associations and social service organizations [@Ye:2021]. Thus, ONGOs obtaining legal identity in this way have to navigate through a legal framework designed for the for-profit institutional logic, e.g, focusing on project investors' right to investment return. 

The legal framework governing ONGOs was overhauled by the Chinese ONGO Law. The new law applies to all Overseas (including Hong Kong, Macau and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of Economic Development, Education, Science, Technology, Culture, Public Health, Sports, Environment Protection, Poverty Alleviation, and Disaster Relief etc. (Article 3). In other words, after the Overseas NGOs became effective, any nonprofit activities conducted by those ONGOs that cannot successfully obtaining proper legal authorization according to the law will be deemed illegal. Specifically, the ONGO law stipulates two ways to lawfully conduct nonprofit activities in China for ONGOs: registering ROs or filing information for documentation of temporary activities with the Ministry of Public Security (“MPS”) and Provincial-level Public Security bureaus, which are the registering and regulatory authority for ONGOs designated by the law. Registering an RO would be lawful identity gaining channel for INGOs seeking for on-going presence in China while temporary activities are suitable for INGOs that need to conduct one-off programs that last no longer than one year. 

This paper studies the the empirical data of the registration of ROs in the years following the enactment of the ONGO Law to uncover the association between INGO issue areas and the composition of successful RO registration and the operational space granted. Registering RO under the ONGO Law requiring the consent of a Chinese professional supervisory unit (the "PSU"), which are governmental or quasi-governmental overseeing the INGO's issue area to co-supervise the INGOs with Public Security bureaus. And it turns out that obtaining the consent of a PSU to apply for registration became a key challenge for ONGOs, because potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. Therefore, the composition of the successfully registered RO inform us whether ROs working on different issue areas have varied level of difficulty in obtaining legal status. Moreover, We measure the later with a proxy of the number of provinces that the ROs are authorized to operate. Specifically, the registration document of an RO would specify the field of work and mission for the RO and list the range of provinces that the RO is authorized to conduct nonprofit activities in (Article 18). Some ROs are authorized to operate across mainland China, which is 32 provincial administrative regions in total, but there are also many that are authorized to operate in one to multiple provinces but not all. We use the number of provinces that ROs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the empirical understanding that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as larger as possible. [@Li:2020]


# Literature and Theoretical Background

## Literature on Closing Space for INGOs

Contentiousness, regime stability, other reasons (to add studies on this construct globally)


## Literature on differenciated attitudes towards INGOs (as reveal in implementation)

"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs. financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]

Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."

*de jure* vs. *de facto* difference "represents a bureaucratic form of repression" [@ChaudhryHeiss:2022]


The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss:2022; @Carothers:2016].  Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017;@TeetsHsu:2016). However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation. A couple of studies [@Jia:2017; @YeHuang:2018)] conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations. However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking. 

This paper aims to fill these gaps by empirically examining how the "closing space" hypothesis applies to China in the years after the ONGO Law took effect. China provides an excellent setting for testing these theories because China's promulgation of restrictive INGO law as an authoritarian jurisdiction fits the observed global trends in recent years, thus can serve as an representative case to deepen scholarly understanding around these themes. Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities, enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*). 

Based on extant literature and theoretical understanding, we hypothesize that the operation space INGOs are granted is associated with the level of contentious their missions, i.e., the issue areas they work in. Since the level of contentious is also manifested by the level of difficulty they face while seeking lawful registration. We also hypothesize that large operational space of INGOs is negatively associated the time elapsed since the law took effect when they successfully got registered. 

The follow section is structured as follow. In the data and methods section, we first report the data cleaning and coding process and measurements used in our empirical analysis. Then we explain the rationale for choosing ordered beta regression to fit our models. In the Results section, we report and interpret both descriptive analysis and regression analysis results. We conclude the paper by discussing the implications of our findings with respective to more general scholarly understanding of the closing space of international civil society. 


# Data and methods

## Data

The data used in this paper was collected from INGOs' public registration documents disclosed by MPS’s Overseas NGO Office on the online service platform for INGOs. We also use ChinaFile's China ONGO data for complementary purpose, we merge in the English organization name in ChinaFile for the sake of transparency of our analysis to broader communities. The data we collected spans from January 1, 2017, when the law took effect, to December 31, 2021, with data for 633 ROs in total. The filing document of ROs disclose the name, the registration date, the registration authority (which public security bureau regulates it), the PSU, the address and issue area or purposes of the RO and the specific provinces they can work in. We code the variables we use in the empirical analysis from the registration information. Most of the coding and data cleaning work is objective data wrangling process, such as parsing out the province each RO is in from the address, or calculating the total number provinces approved in the registration document. Meanwhile, the coding of issue areas are conducted by the authors based on the areas set out Article 3 (specified above) and clustering of the issue areas of the actually registered ROs.  (to cross-validate among authors).


## Measurement 

### Dependent Variables

Our dependent variable is "geo_scope_num", the count of the total number of provinces each RO is authorized to operate in. We derived this variable from the specific list of authorized provinces as recorded in the RO's registration documentation. As discussed above, we use this measurement as a proxy for operational space for INGOs, because any geographical constraints on the RO impacts on the flexibility of the INGO operations. For example, in circumstances where emergency like the COVID 19 pandemic hits, it would be extremely hard for INGOs to plan beforehand which areas would need their service. Thus, we assume INGOs that are not set up with any locally-bound purposes would need to or hope to (if there is not yet such needs) be able to operate in as broader geographical scope as possible. 


### Independent Variables

Our first independent variable is "work_field_code1", the issue area we code from mission statement specified in the RO's registration documentation. Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers (to do). The coding rules for overlapping issue areas can be found in the Appendix (to add). We decided to have 9 issue areas groups based on list of lawful fields of work specified by the Article 3 of the ONGO Law and how actual issue areas cluster for registered ROs. 

Below is the list of issue areas INGOs' registered ROs are coded into.

- **Economy and trade**
- **Environment** (including animal protection)
- **Education** (including youth development)
- **Charity and humanitarian** poverty alleviation, disaster relief, etc., including rural development 
- **Science and technology**
- **Industry association**
- **Health**, public health and health care system support (professional training)
- **Arts and Culture** including sports and international culture exchange
- **General**, usually grant-making organizations, Or working on general international communication, including among governments, or working on multiple fields not overlapping


Our second variable is "time_elapsed". This variable is derived the time difference between ROs' registration date and January 1, 2017 when the law took effect. The longer the time elapsed since registration should be achieved by INGOs, it indicates that it took longer time for them to seek the content of both the PSU and Public Security Bureaus to be their supervisions or regulators and grant them legal identity. 


### Control Variables

Our first control variable is "local_connet". It is a dichotomous variable indicating whether operating locally is built into the RO's mission. There are cases where the aim or mission of the INGO attached to a locality, either having a county or city name in their RO name or purposes, or the INGO are actually set up by people in China and they registered the RO to communicate between the "hometown" and the INGO set up abroad. So we include this variable in our model to how having local connection is associated with the operational space of ROs as well as how the contentious level associates with operation space when we account for this factor. 

We also cluster our 633 RO cases by the province where they are registered in our hierarchical Bayesian modeling. Thus, we account for any variance caused by the socioeconomic and institutional differences in various provinces of China. And the level province is the apporoiate level to cluster because all the ROs are registered at the provincial public security bureaus. 


## Regression Model

Our data provides us with rich descriptive detail of the types of INGOs allowed to register in China following the advent of the ONGO law, and we explore patterns in this data below. In addition to presenting descriptive summary statistics, we create a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility. This approach allows us to hold specific variables constant and generate predictions for hypothetical new, not-yet-registered INGOs, providing us with stronger empirical implications. Additionally, Bayesian modeling allows us to calculate the posterior distribution of our different estimands. Rather than report a single value for the proportion of registered INGOs worked on specific issues, we can estimate posterior credible intervals that represent the probability that the true proportion falls within a specific range. We report posterior medians and 95% credible intervals throughout our analysis. Importantly, these intervals do not behave like more traditional frequentist confidence intervals. Instead, they can be interpreted as the probability that a reported estimate falls within the range, given the data and modeling choices.

```{r fig-province-count-collapsed, fig.width=6, fig.height=3}
#| include: true
#| echo: false
#| fig-cap: "Count of the number of provinces each INGO is authorized to operate in. The left panel shows the full distribution of INGOs registered in 2–31 provinces; the right panel collapses these in-between counts to a single category."
provinces_collapsed <- ongo |> 
  drop_na(province_count) |> 
  mutate(province_count = case_when(
    province_count == 1 ~ "1",
    province_count > 1 & province_count < 32 ~ "2–31",
    province_count == 32 ~ "32"
  ))

p1 <- ggplot(ongo, aes(x = province_count)) +
  geom_histogram(binwidth = 1, size = 0.1, boundary = 0,
                 fill = clrs[6], color = "white") +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  labs(x = "Provinces INGOs are authorized to work in", y = "Count") +
  theme_ongo()

p2 <- ggplot(provinces_collapsed, aes(x = province_count)) + 
  geom_bar(fill = clrs[6]) +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(sec.axis = sec_axis(trans = ~ . / nrow(provinces_collapsed),
                                         labels = label_percent()),
                     breaks = seq(0, 250, 50)) +
  labs(x = NULL, y = NULL) +
  theme_ongo()

(p1 | p2) + 
  plot_layout(nrow = 1, widths = c(0.7, 0.3))
```

Modeling the count of provinces each INGO is authorized to operate in presents a unique statistical challenge. As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2–31 provinces. Our main variable of interest is thus a mix of continuous outcomes (i.e. a range of provinces) bounded between two discrete outcomes (i.e. one province and all provinces). Standard modeling approaches like ordinary least squares regression (OLS) cannot accurately capture the unique features of the data and will generate predictions that fall outside allowable bounds (i.e. negative counts of provinces or more than 32 provinces). If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited outcomes within a 0–1 range. However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1)  and 100% (32). To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], and extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2–31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages. We can thus explore the dynamics of each of our independent variables of interest in multiple ways—we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.

@eq-ordbeta provides a formal definition of our modeling choices. Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables. We also include province-specific random offsets for each intercept to account for between-region differences in how INGOs are regulated. We use weakly informative priors for all model parameters.

::: {.column-page-inset-right}

$$
\begin{aligned}
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\ Beta}(\mu_{i_j}, \phi_y, k_{0_y}, k_{1_y}) & \text{Registered provinces for INGO $i$ in province $j$}\\[8pt]
\mu_{i_j} =&\ (\beta_0 + b_{0_j}) + \beta_1\ \text{Issue area}\ + & \text{Average outcome}\\
&\ \beta_2\ \text{Local connections}\ + \\
&\ \beta_3\ \text{Years since law took effect} \\
b_{0_j} =&\ \mathcal{N}(0, \sigma_0) & \text{Random province offsets} \\[8pt]
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) & \text{Prior for global intercept} \\
\beta_{1..3}\ \sim&\ \mathcal{N}(0, 5) & \text{Prior for global coefficients} \\
\sigma_0\ \sim&\ \operatorname{Student\,t}(3, 0, 2.5) & \text{Prior for between-province variability} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) & \text{Prior for within-province variability} \\
k_{0_y}, k_{1_y}\ \sim&\ \operatorname{Dirichlet}(1, 1, 1) & \text{Prior for 0–continuous and continuous–1 cutpoints} \\
\end{aligned}
$$ {#eq-ordbeta}

:::

# Results


## Descriptive Results




## Regression Results

### Issue area

Following our first empirical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and have more geographic flexibility in operating throughout the country. To explore this, we can take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between. @fig-issue-preds-1 presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values. Several notable trends emerge from the model results. INGOs focused on arts and culture are overwhelming the most likely kind of organization to work nationally—arts and culture organizations are predicted to work in all 32 provinces 80% of the time (with a credible interval of 78–83%) and are only predicted to work in a single province a rare 3–5% of the time. Education-focused INGOs, on the other hand, are the least likely kind of organization to be registered in all 32 provinces and are predicted to do so only 32–38% of the time. Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing 24–29% of the time—at least 10 percentage points higher than any other issue area's predicted proportion. All other issue areas follow roughly the patterns in predictions: the most common outcome is for organizations to work nationally (50–60% of the time), followed by working in at least 2 provinces (25–40% of the time), followed by working in a single province (10–20% of the time). @fig-issue-preds-2 shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously. We can see a similar trend—arts and culture INGOs are predicted to work in 28–30 provinces on average, while education INGOs are only predicted to work in 12–20. All other issues range between 20–28 provinces.

::: {#fig-issue-preds layout-ncol=1}

```{r fig-issue-preds-1, fig.width=6, fig.height=4.5}
#| include: true
#| echo: false
#| fig-subcap: "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis categories sum to 100% across the panels."
preds_issue_plot <- preds_issue |> 
  unnest(preds) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) %>% 
  group_by(outcome, work_field_code1, draw) %>% 
  summarize(count = n()) |> 
  group_by(work_field_code1, draw) |> 
  mutate(prop = count / sum(count)) |> 
  ungroup() |> 
  mutate(work_field_code1 = fct_reorder(work_field_code1, prop))

# preds_issue_plot |> 
#   group_by(outcome, work_field_code1) |>
#   median_qi(prop)

ggplot(preds_issue_plot, aes(x = work_field_code1, y = prop)) +
  stat_pointinterval(color = clrs[5], .width = 0.95, fatten_point = 1) +
  facet_wrap(vars(outcome), ncol = 1, scales = "free_y") +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(labels = label_percent()) +
  labs(x = NULL, y = "Proportion of predictions",
       caption = "Point shows posterior median; lines show 95% credible interval") +
  theme_ongo()
```

```{r fig-issue-preds-2}
#| include: true
#| echo: false
#| fig-subcap: "Distribution of the expectation of posterior predictions. These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
epreds_issue |> 
  mutate(work_field_code1 = fct_reorder(work_field_code1, .epred)) |> 
  ggplot(aes(x = .epred, y = work_field_code1)) +
  stat_halfeye(fill = clrs[5], .width = c(0.8, 0.95)) +
  scale_x_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(8, 32, 4))) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = NULL,
       caption = "Point shows posterior median; lines show 80% and 95% credible intervals") +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

Posterior predictions from ordered Beta regression model, conditional on organization issue area.

:::

### Local connections

In our second empirical expectation, we posit that since INGOs that seek out local connections and that are focused on more local China-specific issues, those organizations should be registered in fewer provinces. The results from our model confirm this expectation. @fig-local-preds-1 shows the distribution of predicted posterior outcomes for 1,000 hypothetical INGOs. Organizations without local connections are predicted to work nationally across all provinces nearly half of the time (with a 95% credible interval of 46–51%), and are predicted to work in two or more provinces 32–37% of the time. These organizations with no local connections or local programmatic focus are only predicted to work in a single province 15–19% of the time. In contrast, INGOs *with* local connections are far more likely to only work in one province (32–38%), or only work in a handful of provinces (36–41%). For these locally-focused organizations, the least common prediction is to work nationally, with only a 23–29% probability. @fig-local-preds-2 shows the posterior distribution of the average number of provinces INGOs are expected to be registered in, conditional on their local connections. The same relationship holds—an INGO without local connections is predicted to work in 19–24 provinces on average, while an organization with local connections is only predicted to work in 8–17. 

```{r fig-local-preds, fig.width=6, fig.height=2.5}
#| include: true
#| echo: false
#| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on having local connections."
#| fig-subcap: 
#|   - "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis categories sum to 100% across the panels."
#|   - "Distribution of the expectation of posterior predictions. These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
preds_local_plot <- preds_local |> 
  unnest(preds) |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) %>% 
  group_by(outcome, local_connect, draw) %>% 
  summarize(count = n()) |> 
  group_by(local_connect, draw) |> 
  mutate(prop = count / sum(count))

# preds_local_plot |>
#   group_by(outcome, local_connect) |>
#   median_qi(prop)
#
# epreds_local |>
#   mutate(.epred = prop_to_provinces(.epred)) |> 
#   group_by(local_connect) |>
#   median_qi(.epred)

ggplot(preds_local_plot, aes(x = local_connect, y = prop)) +
  stat_pointinterval(color = clrs[2], .width = c(0.95), fatten_point = 1) +
  facet_wrap(vars(outcome)) +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(labels = label_percent()) +
  labs(x = NULL, y = "Proportion of predictions",
       caption = "Point shows posterior median; lines show 95% credible interval") +
  theme_ongo()

epreds_local |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  ggplot(aes(x = .epred, y = local_connect)) +
  stat_halfeye(fill = clrs[2], .width = c(0.8, 0.95)) +
  scale_x_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(8, 32, 4))) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = NULL,
       caption = "Point shows posterior median; lines show 80% and 95% credible intervals") +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

INGOs with locally focused missions and connections with local provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader non-local missions have a larger geographic reach. While we cannot precisely tell which direction the causal story works with this phenomenon, we can make some reasonable speculations. It is likely that locally-oriented INGOs purposely network and seek out connections with local PSUs before formally registering, thus fostering better relationships with government officials and furthering the organization's mission within its limited provinces. It is also likely, given the high probability of national reach, that organizations without local connections purposely do not spend the time and effort to cultivate those relationships, as it is not necessary to operate across many provinces. A rival explanation that having local connections reduces an organization's flexibility does not seem warranted. Although INGOs with local connections do have a more limited geographic scope, INGOs appear to purposely limit the number of provinces they work in in order to focus more on their local work.

### Registration timing

# Discussion


# References
