---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
date: "2023-04-07"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
abstract: |
  China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international NGOs (INGOs). However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws. Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations. In this paper, we measure the effect of China’s ONGO law on INGO operations in the five years since the passage of the law. We test whether and how INGO operational space under the ONGO law is influenced by organizations’ issue areas. We argue that the less contensious the issue areas INGOs work in the more likely they are granted greater operational space, measured by thenumber of provinces they are allowed to work in by the registration documentation. China provides an excellent setting for testing the "closing space" and "changing space" theoretical understanding because the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities. We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with multilevel Bayesian models. Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
keywords:
  - international NGOs
  - civil society
  - authoritarianism
  - Chinese ONGO law
bibliography: references.bib
link-citations: true
---

```{r setup, include=FALSE}
if (is.null(knitr::pandoc_to())) {
  fmt_out <- "interactive"
} else {
  fmt_out <- knitr::pandoc_to()
}

knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
                      warning = FALSE, message = FALSE)

knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                      fig.width = 6, fig.height = (6 * 0.618),
                      out.width = "80%", collapse = TRUE)

options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r libraries-data}
library(tidyverse)
library(scales)
library(lubridate)
library(tidybayes)
library(marginaleffects)
library(patchwork)
library(kableExtra)
library(gt)
library(targets)

tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

# Generated via random.org
set.seed(8511)

# Load targets 
tar_load(ongo)
tar_load(ongo_mapdata)

# Plotting and modelsummary functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
```

In recent decades, there has been a global tend of “closing space” for civil society across jurisdictions such as Russia, India and Vietnam.[@DupuyPrakash:2020;@ChaudhryHeiss:2020] (*to add citation*) The manifestation of such trend is rolling out restrictive laws that regulate international NGOs (INGOs).[@DupuyPrakash:2020; @ChaudhryHeiss:2022] China’s promulgation of the Law of the People’s Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China (the “ONGO Law”) on April 28, 2016 was considered part of a global wave of legal restrictions on INGOs. The purpose of this study is to empirically examine how the ONGO law has impacted INGO's presence as well as the operational space after the law took effect. By inquiring the *de facto* implementation of the law in addition to formal *de jure* regulations, we will be able to see a more comprehensive picture of the operational space for INGOs. It will also inform as the evolving theorization of the "closing space" and dual attitudes towards INGOs hold true for an Authoritarian jurisdiction such as China. 


ONGO law, what has it meant for ONGOs—how are they responding? [@ChaudhryHeiss:2022]

@FaridLi:2021

Charity law + ONGO law happened at the same time - lots of discussion about what it would mean for ONGOs at the time - lots of people looked at the framework of the law, but we don't know what it has actually looked like
Following up with the actual implementation of law



# Context of the ONGO law

In recent decades, ONGOs came to China after the Reform and Opening-up policy was adopted by the authority and have been playing pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China’s domestic nonprofit sector [@Yin:2009]. Before the promulgation of the ONGO Law, the regulation of ONGOs in China was obscure [Shieh:2018]. The only legal document relevant to ONGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices (“ROs”) of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs. However, the actual application of the regulation was very limited. Up until the ONGO Law took effect on January 1, 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs according to the Regulation on the Management of Foundations, while some Chinese officials estimated in 2016 that there were roughly over 7000 ONGOs operating in China [@YeHuang:2018]. 

Many ONGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China[@Han:2011]. They choose to have a formal legal identity for the convenience such as signing labor contracts directly with employees. However, the legal form of foreign-funded company is not quite compatible with the nature of ONGOs. Under the Chinese legal system, enterprises should be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms for them — foundations, associations and social service organizations [@Ye:2021]. Thus, ONGOs obtaining legal identity in this way have to navigate through a legal framework designed for the for-profit institutional logic, e.g, focusing on project investers' right to investment return. 

The legal framework governing ONGOs was overhauled by the Chinese ONGO Law. The new law applies to all Overseas (including Hong Kong, Macau and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of Economic Development, Education, Science, Technology, Culture, Public Health, Sports, Environment Protection, Poverty Alleviation, and Disaster Relief etc. (Article 3). In other words, after the Overseas NGOs became effective, any nonprofit activities conducted by those ONGOs that cannot successfully obtaining proper legal authorization according to the law will be deemed illegal. Specifically, the ONGO law stipulates two ways to lawfully conduct nonprofit activities in China for ONGOs: registering ROs or filing information for documentation of temporary activities with the Ministry of Public Security (“MPS”) and Provincial-level Public Security bureaus, which are the registering and regulatory authority for ONGOs designated by the law. Registering an RO would be lawful identity gaining channel for INGOs seeking for on-going presence in China while temporary activities are suitable for INGOs that need to coduct one-off programs that last no longer than one year. 

This paper will study the the empirical data of the registration of ROs in the years following the enactment of the ONGO Law to uncover the association between ONGO issue areas and the composition of successful RO registration and the operational space granted.

Registering RO under the ONGO Law requiring the consent of a Chinese professional sponsoring unit (the "PSU"), which are governmental or quasi-governmental overseeing the INGO's issue area to co-supervise the INGOs with Public Security bureaus. And it turns out that obtaining the consent of a PSU to apply for registration became a key challenge for ONGOs, because potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. Therefore, the composition of the successfully registered RO inform us whether ROs working on different issue areas have varied level of difficulty in obtaining legal status. Moreover, We measure the later with a proxy of the number of provinces that the ROs are authorized to operate. Specifically, the registration document of an RO would specify the field of work and mission for the RO and list the range of provinces that the RO is authorized to conduct nonprofit activities in (Article 18). Some ROs are authorized to operate across mainland China, which is 32 provincial administrative regions in total, but there are also many that are authorized to operate in one to multiple provinces but not all. 




# Literature and Theoretical Background

## Literature on Closing Space for INGOs

Contentiousness, regime stability, other reasons

- on how Chinese ONGO Law is seen as part of this trend

The promulgation of China’s ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down International NGOs [@ChaudhryHeiss2022; @Carothers:2016]. (*to update*) Studies on the law has been focused on discussing the historical and political impetus of passing the law (Shieh, 2018) or analyzing the regulatory regimes it that has established and potential implications for ONGOs operating in China [@Feng:2017;@TeetsHsu:2016). However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs’ operations and projects have been affected by the law after successfully gaining legal registration and documentation. A couple of studies [@Jia2017; @YeHuang:2018)] conducted reflections on the first year’s implementation of China’s ONGO Law, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations. However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking. 


## Literature on implementation - de jure vs. de facto differences


## Literature on differenciated attitudes towards INGOs (*maybe merge with literature on implementation?*)

"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs. financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]

Also, [@Plantan2022]





# Theory / research questions

This aims to examin how the "closing space" hypothesis plays out in China. China provides an excellent setting for testing our claim—the 2017 ONGO law regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities. 


- RQ1: Provinces and work field - connects to NGO contentiousness bc everything is noncontentious
- RQ2: Provinces and PSUs - local vs. national - there's variance in local PSUs - flexibility, venue-seeking maybe
- RQ3: Provinces and length of time in country / registration date/year - earlier organizations work in more? - flexibility bc more local knowledge, more interest, more support from government to get registered, etc.


# Data and methods

## Data

The data used in this paper was collected from INGOs' public registration documents disclosed by MPS’s Overseas NGO Office on the online service platform for INGOs. We also use ChinaFile's China ONGO data for complementary purpose, we merge in the English organization name in ChinaFile for the sake of transparency of our analysis to broader communities. The data we collected spans from January 1, 2017, when the law took effect, to December 31, 2021, with data for 633 ROs in total. The filing document of ROs disclose the name, the registration date, the registration authority (which public security bureau regulates it), the PSU, the address and issue area or purposes of the RO and the specific provinces they can work in. We code the variables we use in the empirical analysis from the registration information. Most of the coding and data cleaning work is objective data wrangling process, such as parsing out the province each RO is in from the address, or calculating the total number provinces approved in the registration document. Meanwhile, the coding of issue areas are conducted by the authors based on the areas set out Article 3 (specified above) and clustering of the issue areas of the actually registered ROs.  (to cross-validate among authors).


## Measurement 

### Dependent Variables

- `geo_scope_num`

Count of the number of provinces each RO is authorized to operate in 


### Independent Variables

- `work_field` 

`work_field` is the original mission statement in Chinese. The name "field" is chosen for the moment, because it seems "area" is more easily to be confused with the geographical scope. It is not called "mission" to differentiate from the mission of the mother organization which is not subject to approval of the authority. Also, the statement of the work field tends to be more concrete than missions. 

`work_field_code1` is the main work field code

Based on the issue areas listed by the ONGO Law and how the work fields of registered NGO ROs cluster**

- **[Economy and trade]**

- **[Environment]** (including animal protection)

- **[Education]** (including youth development and international cultural exchange)

- **[Charity and humanitarian]** poverty alleviation, disaster relief, etc., including rural development and social work
  If rural development is researched at the macroeconomics level, coded as science and technology, eg. #375
  
- **[Science and technology]**

- **[Industry association]**

- **[Health]** public health and health care system support (professional training)

- **[Arts and Culture]** including sports (noted as “sports” in `work_field_code2`) and international culture exchange

- **[General]** usually grant-making organizations, Or working on general international communication, including among governments, Or working on multiple fields not overlapping


- `time_elapsed`

This variable is derived the time difference between ROs' registration date and January 1, 2017 when the law took effect. The longer the time elapsed since registration should be achieved by INGOs, it indicates that it took longer time for them to seek the content of both the PSU and Public Security Bureaus to be their supervisions or regulators and grant them legal identity. 


### Control Variables


- `still_active`, `FALSE` for those have indeed de-register and `TRUE` otherwise.


- `home`

home county or region of the ONGO. Not using the name "country" to be flexible enough to denote, Hong Kong, Macau and Taiwan

- `psu_level`

Dummy variable indicating whether the official sponsoring unit (for registration and annual audit) is at the national or local level. 
It is clearly correlated with `geo_scope_num`, but should be a mediating factor for the relationship we are examining. 

- `ro_count`

There are cases where ONGOs are not granted to operate across China, so they register multiple ROs to cover enough number of provinces where they need to work. 

- `local_connect`
There are cases where the aim/mission of the ONGO is attached to a locality, either having a county/city name in their RO name or purposes, or the INGO are actually set up by people in China and they RO to communicate between the "hometown" and the INGO







*Notes to delete:*


No control/pre-group - this is all descriptive about the "after" group of ONGOs that all selected themselves into the regulations



multiple_id - either treat it as a random organization effect for the parent org, or weight it, so if there are 8, we weight by 1/8
cn_background = Chinese NGOs
To compensate such limitation, ONGOs are allowed to register multiple ROs within mainland China at the meantime.



Main assumption: We're interested in the potential to be in other provinces, even if an organization is small now, they want to someday spread out

## Regression Model

Our data provides us with rich descriptive detail of the types of INGOs allowed to register in China following the advent of the ONGO law, and we explore patterns in this data below. In addition to presenting descriptive summary statistics, we create a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility. This approach allows us to hold specific variables constant and generate predictions for hypothetical new, not-yet-registered INGOs, providing us with stronger empirical implications. Additionally, Bayesian modeling allows us to calculate the posterior distribution of our different estimands. Rather than report a single value for the proportion of registered INGOs worked on specific issues, we can estimate posterior credible intervals that represent the probability that the true proportion falls within a specific range. We report posterior medians and 95% credible intervals throughout our analysis. Importantly, these intervals do not behave like more traditional frequentist confidence intervals. Instead, they can be interpreted as the probability that a reported estimate falls within the range, given the data and modeling choices.

```{r fig-province-count-collapsed, fig.width=6, fig.height=3}
#| include: true
#| echo: false
#| fig-cap: "Count of the number of provinces each INGO is authorized to operate in. The left panel shows the full distribution of INGOs registered in 2–31 provinces; the right panel collapses these in-between counts to a single category."
provinces_collapsed <- ongo |> 
  drop_na(province_count) |> 
  mutate(province_count = case_when(
    province_count == 1 ~ "1",
    province_count > 1 & province_count < 32 ~ "2–31",
    province_count == 32 ~ "32"
  ))

p1 <- ggplot(ongo, aes(x = province_count)) +
  geom_histogram(binwidth = 1, size = 0.1, boundary = 0,
                 fill = clrs[6], color = "white") +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  labs(x = "Provinces INGOs are authorized to work in", y = "Count") +
  theme_ongo()

p2 <- ggplot(provinces_collapsed, aes(x = province_count)) + 
  geom_bar(fill = clrs[6]) +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(sec.axis = sec_axis(trans = ~ . / nrow(provinces_collapsed),
                                         labels = label_percent()),
                     breaks = seq(0, 250, 50)) +
  labs(x = NULL, y = NULL) +
  theme_ongo()

(p1 | p2) + 
  plot_layout(nrow = 1, widths = c(0.7, 0.3))
```

Modeling the count of provinces each INGO is authorized to operate in presents a unique statistical challenge. As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2–31 provinces. Our main variable of interest is thus a mix of continuous outcomes (i.e. a range of provinces) bounded between two discrete outcomes (i.e. one province and all provinces). Standard modeling approaches like ordinary least squares regression (OLS) cannot accurately capture the unique features of the data and will generate predictions that fall outside allowable bounds (i.e. negative counts of provinces or more than 32 provinces). If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited outcomes within a 0–1 range. However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1)  and 100% (32). To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], and extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2–31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages. We can thus explore the dynamics of each of our independent variables of interest in multiple ways—we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.

@eq-ordbeta provides a formal definition of our modeling choices. Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables. We also include province-specific random offsets for each intercept to account for between-region differences in how INGOs are regulated. We use weakly informative priors for all model parameters.

::: {.column-page-inset-right}

$$
\begin{aligned}
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\ Beta}(\mu_{i_j}, \phi_y, k_{0_y}, k_{1_y}) & \text{Registered provinces for INGO $i$ in province $j$}\\[8pt]
\mu_{i_j} =&\ (\beta_0 + b_{0_j}) + \beta_1\ \text{Issue area}\ + & \text{Average outcome}\\
&\ \beta_2\ \text{Local connections}\ + \\
&\ \beta_3\ \text{Years since law took effect} \\
b_{0_j} =&\ \mathcal{N}(0, \sigma_0) & \text{Random province offsets} \\[8pt]
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) & \text{Prior for global intercept} \\
\beta_{1..3}\ \sim&\ \mathcal{N}(0, 5) & \text{Prior for global coefficients} \\
\sigma_0\ \sim&\ \operatorname{Student\,t}(3, 0, 2.5) & \text{Prior for between-province variability} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) & \text{Prior for within-province variability} \\
k_{0_y}, k_{1_y}\ \sim&\ \operatorname{Dirichlet}(1, 1, 1) & \text{Prior for 0–continuous and continuous–1 cutpoints} \\
\end{aligned}
$$ {#eq-ordbeta}

:::

# Results


## Descriptive Results




## Regression Results

### Issue area


### Local connections

In our second empirical expectation, we posit that since INGOs that seek out local connections and that are focused on more local China-specific issues, those organizations should be registered in fewer provinces. The results from our model confirm this expectation.

TODO 12ish expected provinces for INGOs with no local connections; 21ish for INGOs with local connections

TODO We can take advantage of the continuous + discrete features of ordered beta and see BLAH BLAH. After simulating 1,000 hypothetical new INGOs, organizations without local connections are predicted to work nationally in all provinces nearly 50% of the time (ASDF-ASDF credible interval), and are predicted to work in 2 or more provinces 35% of the time. These organizations with no local connections or local programmatic focus are only predicted to work in a single province 15ish% of the time. In contrast, INGOs *with* local connections are far more likely to only work in one province (35%), or only work in a handful of provinces. These locally-focused organizations are only predicted to work nationally 25% of the time. 

TODO Graphs


### Registration timing

# Discussion


# References
