---
title: "The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society"
short-title: "China's ONGO Law and International Civil Society"
date: "2023-09-25"
author:
- name: Meng Ye
  affiliation: Georgia State University
  email: mye2@student.gsu.edu
  orcid: 0000-0002-6552-8338
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
abstract: |
  China’s 2017 Overseas NGO (ONGO) Law is part of a larger global trend of legal restrictions on international nongovernmental organizations (INGOs). However, the effects of this global crackdown on INGOs have been difficult to measure since there is often divergence between the formal de jure regulations and the de facto implementation of these laws. Additionally, the severity and consistency of the enforcement of these laws often depends on the type of services provided by these organizations. In this paper, we explore the effect of China’s ONGO law on INGO operations in the five years since the passage of the law. We test whether and how INGO operational space under the ONGO law is influenced by organizations' issue areas. We argue that the less contentious the issue areas INGOs work in the more likely they are granted greater operational space, measured by the number of provinces they are legally authorized to work in. China provides an excellent setting for examining the phenomenon of closing space civic space, since the 2017 ONGO law hypothetically regulates both claim-making and service-providing NGOs, while the level of ambiguity of the law gives ample room for arbitrary discretion and conflicting attitudes by authorities. We test our argument by analyzing administrative data from 633 registered representative offices of INGOs registered in China between 2017–2021 and test our hypothesis with a multilevel Bayesian model. Our results speak to the broader literature on closing civic space and provide an empirical illustration of the practical effect of NGO restrictions on global civil society.
keywords:
  - international NGOs
  - civil society
  - authoritarianism
  - Chinese ONGO law
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.bib
link-citations: true
---

```{r setup, include=FALSE}
if (is.null(knitr::pandoc_to())) {
  fmt_out <- "interactive"
} else {
  fmt_out <- knitr::pandoc_to()
}

knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
                      warning = FALSE, message = FALSE)

knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                      fig.width = 6, fig.height = (6 * 0.618),
                      out.width = "100%", collapse = TRUE)

options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r libraries-data}
library(tidyverse)
library(scales)
library(lubridate)
library(tidybayes)
library(sf)
library(ggrepel)
library(marginaleffects)
library(tidygraph)
library(ggraph)
library(patchwork)
library(kableExtra)
library(gt)
library(targets)

tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

# Generated via random.org
set.seed(8511)

# Load targets 
tar_load(c(ongo, ongo_mapdata))
tar_load(c(preds_issue, preds_local, preds_timing,
           epreds_issue, epreds_local, epreds_timing,
           epreds_timing_local, issue_indicator_lookup))

# Plotting and modelsummary functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
set_annotation_fonts()
```

::: {.content-visible when-format="html"}
# Introduction {.hide}
:::

In the past decade, nearly 100 countries have proposed or enacted legal measures designed to restrict civil society [@ICNL:2021], and only 21% of countries have open and unrestricted civic space [@ChaudhryHeiss:2022a; @Civicus:2023]. This global trend of closing or shrinking civic space [@Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016] has affected countries of all regime types, including both autocracies and democracies such as Morocco and Palestine [@AtiaHerrold:2018], India [@press-trust-india:2019], Vietnam [@Sidel:2023], Canada [@CIVICUS:2013], and the United States [@Cramer:2020]. On April 28, 2016, China passed its own set of legal restrictions on civil society with its Law of the People's Republic of China on Administration of Activities of Overseas Nongovernmental Organizations in the Mainland of China, or "ONGO Law," which formally took effect on January 1, 2017. The law requires all international NGOs (INGOs) to either register representative offices (ROs) or file temporary activities to lawfully operate in mainland China.As an authoritarian state with a growing nonprofit sector, the Chinese model of implementing restrictive laws for international NGOs (INGOs) has important implications for understanding the dynamics of how civil society laws can be used as policy tools to harness INGOs.

TODO: Andrew - update and coordinate the introductory paragraphs with the theoretical framing below

*Meng's notes/suggestions*: to highlight the theoretical significance in the very beginning (just listing the idea pool for moment, not concise enough):

 1. A frequently approach to close the space of INGOs is passing restrictive laws/institutional approach. [@DeMattee:2019]. To further understanding this global phenomena , China is an important case to explore the impacts such restrictive laws have on the operation of INGOs. Such legal restrictions can be either direct (denial of legal access/cannot register) or covert (red-tape, requiring the approval of PSUs, or the uncertainty of having to filing TAs case by case)
 
 2. *de facto* vs. *de jure* (incorporating the paragraph below) and differentiated treatment for more vs. less contentious INGOs. Authoritarian -> arbitrary and varied application of the law -> different *operating space*
 
 3. Laws and policies as a *policy tool* and behavioral shifit: to tame INGO to be more cooperative to government. The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly. 
 
The impacts on international civil society  we examine include not only access or representation of INGOs in China, but also whether there is change of behaviors [@WuNie:2021]. Mention the concept of *flexibility (in the sense of adjusting to change)* too?
 

The purpose of this study is to empirically examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China since 2017, and in particular how the ONGO Law has shaped the operational space allowed for INGO operations in the country. By examining the *de facto* implementation of the law in addition to its formal *de jure* regulations, we provide a more comprehensive and data-based picture of the operational space for INGOs. By relying on representative empirical data from mainland China, our study also contributes to a growing body of research on the effects of closing civic space on INGO behavior and strategies.

This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines the association between INGO issue areas and the operational space granted to them in the country. Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. INGOs vary in their ability to attract partner PSUs, and organizations that are unable to find corresponding PSUs are more limited in their geographic reach within the country. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province. We use the number of provinces that INGOs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the assumption that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as large as possible [@Li:2020].

In this paper, we first explore existing theories of closing civic space, authoritarian regulation of civil society, and differential regulation of international vs. domestic NGOs. We then propose a set of empirical expectations for INGOs registering in China following the 2017 ONGO Law. We describe our data, which includes registration and organization-level details for all 633 INGOs registered between January 1, 2017 and December 31, 2021, and our descriptive and empirical approach to analyzing the data. We then present the findings from our data, exploring each of our empirical expectations, and conclude with a discussion of how these results connect to larger themes of the global closure of civic space.


In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs. We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is *organizational flexibility*, or the ability to operate with greater latitude in host countries. We propose two key determinants of this flexibility: (1) organizational characteristics and (2) host government preferences and relationships TODO and their interplay/interaction. We illustrate this theory using the case of China TODO stats and case studies, mixed method, demonstrating how INGOs that address issues that align with government preferences enjoy the most organizational flexibility in the country.


# Closing civic space

## The global constriction of civic space

## The "closing space" phenomenon

Many different reasons for these restrictions and several purposes - INGOs pose a threat to regime stability, but they also provide governments with services and technical expertise. Civil society/CSO/NGO + host government definition - De Mattee and institutional taxonomy. My stuff on gatekeeping vs. program capture.

INGO regulations are implemented and enforced differentially - difference in de jure and de facto. This differential enforcement is one mechanism to allow host governments to harness the aspects of INGO programming that align with their domestic policy preferences while limiting INGO behavior that could threaten regime stability. 

Why pass laws in the first place and why enforcement differently?

@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations---the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015]. See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]

"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs. financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]

Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."

The presence of de jure regulations and the strictness of their de facto enforcement are both determined by the interplay between INGO characteristics and government preferences.

Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].

Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]



## Closing civic space in China

China provides a fascinating example of both authoritarian preferences for INGO regulations and INGO adaptations to these regulations. 


3. Laws and policies as a *policy tool* and behavioral shifit: to tame INGO to be more cooperative to government. The requirement of PSU and Chinese partner to re-direct INGOs to be more authority friendly. 

Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011; @HolbigLang:2022; @Yin:2009]. However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs. Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, including foundations, associations, and social service organizations [@Ye:2021]. Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on protecting investors' right to investment returns.


This paper explores the characteristics of all registered INGOs in China in the five years after the ONGO Law became effective and examines the association between INGO issue areas and the operational space granted to them in the country. Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. INGOs vary in their ability to attract partner PSUs, and organizations that are unable to find corresponding PSUs are more limited in their geographic reach within the country. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province. We use the number of provinces that INGOs are authorized to work in as a proxy to measure the operational space for INGOs in China based on the assumption that INGOs need to or hope to have the approval to be able to carry out their programs in a geographical scope as large as possible [@Li:2020].

In this paper, we first explore existing theories of closing civic space, authoritarian regulation of civil society, and differential regulation of international vs. domestic NGOs. We then propose a set of empirical expectations for INGOs registering in China following the 2017 ONGO Law. We describe our data, which includes registration and organization-level details for all 633 INGOs registered between January 1, 2017 and December 31, 2021, and our descriptive and empirical approach to analyzing the data. We then present the findings from our data, exploring each of our empirical expectations, and conclude with a discussion of how these results connect to larger themes of the global closure of civic space.


# Legal background

International NGOs began to play an important role in China in the early 1990s as part of the country's Reform and Opening-Up policy, and organizations like Save the Children and the Ford Foundation established local offices and branches. Since then, INGOs and global civil society have played pivotal roles in providing funding, organizational and program management skills, as well as catalytic support for the emergence of China's domestic nonprofit sector [@Yin:2009]. Prior to the implementation of the 2017 ONGO Law, regulation of INGOs in China was obscure [@Shieh:2018; @Spires:2022]. The only legal document relevant to INGOs was a section of the Regulation on the Management of Foundations by the State Council that specifies the registration of representative offices ("ROs") of foreign foundations with the Ministry of Civil Affairs, the regulator of Chinese domestic NGOs. However, the actual application of the regulation was very limited. Up until the ONGO Law took effect in 2017, there were fewer than 30 foreign foundation ROs registered at the Ministry of Civil Affairs, while some Chinese officials estimated in 2016 that there were roughly over 7,000 INGOs operating in China [@YeHuang:2018].

Many INGOs gained legal identity within mainland China using the vehicle of foreign-funded companies [@Sidel:2016], though there were no clear requirements for them to have a formal legal presence in China [@Han:2011; @HolbigLang:2022; @Yin:2009]. However, the legal form of foreign-funded company is not quite compatible with the nonprofit nature of INGOs. Under the Chinese legal system, enterprises are intended to be for-profit entities and nonprofit organizations are required to choose other stand-alone legal forms, including foundations, associations, and social service organizations [@Ye:2021]. Thus, INGOs obtaining legal identity in this way have to navigate through a legal framework designed for a for-profit institutional logic, e.g, focusing on protecting investors' right to investment returns.

The legal framework governing INGOs was overhauled by the 2017 Chinese ONGO Law. The new law applies to all overseas (including Hong Kong, Macau, and Taiwan) non-governmental organizations that conduct not-for-profit activities in the fields of economic development, education, science, technology, culture, public health, sports, environment protection, poverty alleviation, and disaster relief (Article 3). The ONGO Law stipulates two ways for INGOs to lawfully conduct nonprofit activities in China: (1) submitting an application for formal permanent registration, or (2) filing documentation of temporary activities with the Ministry of Public Security and provincial-level Public Security Bureaus, which are the registering and regulatory authority for INGOs. Formal registration of an RO allows them to maintain an ongoing present in the country, while temporary activities are intended for INGOs that need to conduct one-off programs that last no longer than one year. Abiding by these two channels to obtain lawful presence is mandatory for INGOs after the Overseas NGO Law came into effect, any INGOs that could not successfully obtain proper legal authorization would be deemed illegal.

TODO: Meng - add brief explanations of the TA/RO pathways figure and articulate the "cooperative requirements part", i.e., seeking a psu or Chinese partner

TODO: Andrew - image of TA/RO pathways @fig-ro-ta-pathways

```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Two possible pathways for international NGOs to legally work in 
#|   China under the 2017 ONGO law, either as formal Registered Organizations 
#|   (ROs) or by undertaking specific Temporary Activities (TAs)"
ro_nodes <- tibble(
  step = c(
    "Find a professional supervisory unit (PSU)",
    "Obtain PSU approval",
    "Open organization bank accounts",
    "Keep programming within approved scope",
    "Submit annual work plans to PSU and Public Security Bureau",
    "Submit annual reports to PSU and Public Security Bureau"
  ),
  type = "Registered organization (RO)"
)
ro_edges <- tibble(from = 1:5, to = 2:6)
ro_graph <- tbl_graph(nodes = ro_nodes, edges = ro_edges)

ta_nodes <- tibble(
  step = c(
    "Find an eligible Chinese partner to file paperwork",
    "Obtain PSU approval",
    "Channel money through partner’s bank",
    "Keep programming within approved scope",
    "Finish work within a year",
    "Submit final project report to Public Security Bureau"
  ),
  type = "Temporary activities (TA)"
)
ta_edges <- tibble(from = 1:5, to = 2:6)
ta_graph <- tbl_graph(nodes = ta_nodes, edges = ta_edges)

combined_graph <- bind_graphs(ro_graph, ta_graph)

ggraph(combined_graph, layout = "tree") +
  geom_node_label(
    aes(x = x, y = y, label = step), 
    size = 2.5, label.r = unit(0, units = "pt")
  ) +
  geom_edge_link(
    aes(
      start_cap = label_rect(node1.step, padding = margin(5, 5, 5, 5, "pt")),
      end_cap = label_rect(node2.step, padding = margin(5, 5, 5, 5, "pt"))
    ),
    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
    edge_linewidth = 0.25
  ) +
  facet_nodes(vars(type), scales = "free_x") +
  labs(x = NULL, y = NULL) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
    strip.text = element_text(hjust = 0.5)
  )
```



# Theoretical background and expectations

TODO: Andrew: This 2017 law fits with a broader global phenomenon of closing civic space… General crackdown stuff + China crackdown stuff + our addition

China's 2017 ONGO Law has been discussed by scholars mostly as a part of a global trend of restricting and cracking down on international NGOs [@ChaudhryHeiss:2022; @Carothers:2016]. Studies on the law has been focused on discussing the historical and political impetus of passing the law [@Shieh:2018] or analyzing the regulatory regimes it that has established and potential implications for INGOs operating in China [@Feng:2017; @TeetsHsu:2016]. However, little work has been done to examine the actual implementation situation of this law, and how the dynamics of ONGOs' operations and projects have been affected by the law after successfully gaining legal registration and documentation. A few studies [@Jia:2017; @YeHuang:2018] have reflected on the implementation of the ONGO Law after its first year, including the initial phase of drafting and refining implementing regulations and promotion, as well as training sessions conducted by Public Security Bureaus in different locations. However, a more up-to-date and comprehensive understanding of the effects of the ONGO law is still lacking.

This paper aims to fill these gaps by empirically examining how the "closing space" hypothesis applies to China in the years after the ONGO Law took effect. China provides an excellent setting for testing these theories because China's promulgation of restrictive INGO law as an authoritarian jurisdiction fits the observed global trends in recent years, thus can serve as an representative case to deepen scholarly understanding around these themes. Also, the level of ambiguity of the legal framework gives ample room for arbitrary discretion and conflicting attitudes by authorities[@Jia:2017], enabling us to analyze rules in form (*de jure*) as well as rules in use (*de facto*).

## The "closing space" phenomenon

Contentiousness, regime stability, other reasons [see @Chaudhry:2022; @ChaudhryHeiss:2021; @CarothersBrechenmacher:2014; @DupuyPrakash:2018; @DupuyPrakash:2020; @DupuyRonPrakash:2016].

Main idea: organizations that work on more contentious issues like human rights advocacy face stricter regulations [@Bush:2015; @ChaudhryHeiss:2021]

(Meng added)

## De jure vs. de facto implementation of civil society regulations

@ChaudhryHeiss:2022 and the divergence in de jure and de facto regulations---the implementation doesn't have to match the written law, and often the written law can serve as a "weapon hanging on the wall that never fires" that serves as a warning to potentially uncooperative NGOs [@Kozenko:2015]. See also [@ToeplerZimmerFrohlich:2020; @Plantan:2022]

::: content-hidden
"We discuss the role of civil society organizations (CSOs) as agents of democratization and note the emergence of dual, at times apparently conflicting policy postures within authoritarian regimes (restriction and repression for some CSOs vs. financial support and opportunities for collaboration for others)." [@ToeplerZimmerFrohlich:2020]

Also, [@Plantan:2022] finds "that I find" evidence of selective implementation that reveals which groups are seen as threatening or beneficial."
:::


## China's INGO as a policy tool

*note* changed the sub-title to incorporate the policy tool lense too. 

TODO: Meng - China crackdown lit


## Empirical expectations

See @fig-theory

```{r fig-theory, fig.width=6, fig.height=2}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Diagram of our theoretical framework showing three possible determinants of INGO operational flexibility: the contentiousness of the INGO's issue area, the inherent geographic scope of the INGO's operations, and the government's interest in and relationship with the INGO."
theory_nodes <- tribble(
  ~id, ~name, ~x, ~y, ~highlight,
  1,   "Issue contentiousness", 1, 0, FALSE,
  2,   "Operational flexibility", 3, 0, TRUE,
  3,   "Local focus", 2, 1, FALSE,
  4,   "Government preferences", 2, -1, FALSE
)

theory_edges <- tribble(
  ~from, ~to,
  1, 2,
  3, 1,
  3, 2,
  1, 4,
  4, 1,
  4, 2
)

theory_graph <- tbl_graph(nodes = theory_nodes, edges = theory_edges, directed = TRUE)

ggraph(theory_graph, x = x, y = y) + 
  geom_edge_link(
    aes(
      start_cap = label_rect(node1.name, padding = margin(10, 5, 10, 5, "pt")),
      end_cap = label_rect(node2.name, padding = margin(10, 5, 10, 5, "pt"))
    ),
    arrow = arrow(angle = 30, length = unit(6, "pt"), type = "closed"),
    edge_linewidth = 0.25
  ) +
  geom_node_label(
    aes(x = x, y = y, label = name, fill = highlight), 
    size = 3, label.r = unit(0, units = "pt"), fontface = "bold"
  ) +
  scale_x_continuous(expand = expansion(add = 0.3)) +
  scale_y_continuous(expand = expansion(add = 0.2)) +
  scale_fill_manual(values = c("white", clrs[1]), guide = "none") +
  labs(x = NULL, y = NULL) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
  )
```


Based on this framework, we can identify and test several theoretical expectations:

Based on extant literature and theoretical understanding, we argue that the operation space INGOs are granted is associated with the level of contentiousness their missions, i.e., the issue areas they work in. Since the level of contentiousness is also manifested by the level of difficulty they face while seeking lawful registration.


In 2018 Batke and Hang posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences. @HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift[ed] towards fields of activity high up the government’s domestic policy agenda" [-@HolbigLang:2022, p. 587].

Following our theory, government preferences thus directly influence INGO issue areas, which in turn shapes the amount of flexibility enjoyed by the INGO. Accordingly, we expect that INGOs working on non-contentious, regime-aligned issues will have greater reach throughout the country:

- **Theoretical expectation 1**: Because they are seen as less of a threat to regime stability and more aligned with government policy preferences, INGOs working on less contentious issues should be registered in more provinces.



Relationships with PSUs are a critical part of the INGO registration process. No PSU is obligated to take on a supervisory role for an INGO, and interested organizations have to cultivate relationships with local officials. Accordingly, many of the INGOs we observe in our data either demonstrate close connections with local governmental authorities or frame their activities and services with a narrower geographic scope.

Using the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility and reach might not reflect reality. Some INGOs explicitly limit their operations to specific provinces, either because their programming is more tailored to local conditions, or because they do not feel a need to go through the longer process of obtaining national-level registration. Accordingly, we temper our issue area expectation with a measure of explicitly local purpose. Organizations that have no intention of registering nationally should be registered in fewer provinces:

- **Theoretical expectation 2**: Because they are explicitly focused on local issues, INGOs with explicitly local missions should be registered in fewer provinces.

Finally, we also expect that the operational space for INGOs is negatively associated with the time elapsed since the law took effect. The mechanism behind this expectation is directly related to both issue area and government preferences.

- **Theoretical expectation 3** (registration timing): Because formal registration can take a long time and can involve many bureaucratic hurdles, INGOs that registered soon after the law took effect should be be (1) less of a threat and (2) a higher priority for processing, and so should be registered in more provinces.


# Data and empirical approach

Main structure for these expectations + our analysis:

We test these theoretical expectations using a mixed methods approach. Using 

- Stats + case study: **Flexibility**
- Stats + case study: **Contentiousness**
- Case study: **Relationship with PSU and government** (stats/descriptive bc lots of chambers of commerce

## Data

The data used in this paper was collected from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office online service platform. The platform is a website maintained by the registrar of INGOs and regularly publicize the administrative documentation of all the ROs and temporary activities registered or filled across China. The data used in this study spans from January 1, 2017, when the law took effect, to December 31, 2021, with information for all 633 registered organizations approved as of the cutoff point. The filing documents for ROs disclose the name, the address, the registration date, the registration authority (which public security bureau regulates it), the PSU, the issue area or purposes of the RO, and the specific provinces they can work in. We merge our INGO data with additional data of Chinese INGO data from ChinaFile, a project that translate and code the MPS platform data, to include their English organization names, for the sake of transparency and accessibility.

We code the variables we use in the empirical analysis from the registration information. Most of our data cleaning work is an objective data wrangling process, such as parsing out the province each RO registered in from the address, or calculating the total number provinces approved in the registration document. Meanwhile, the qualitative coding of issue areas is conducted by the authors, based on consistent coding rules agreed by the authors.

## Measurement

### Dependent variable

Our dependent variable is the count of the total number of provinces each INGO is authorized to operate in. We derived this variable from the specific list of authorized provinces as recorded in the RO's registration documentation. As discussed above, we use this measurement as a proxy for operational space for INGOs, because any geographical constraints on the RO impacts on the flexibility of the INGO operations. For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas would need their service. Thus, we assume INGOs that are not set up with any locally-bound purposes would need to or hope to (if there is not yet such need) be able to operate in as broad a geographical scope as possible.

### Independent variables

Our key independent variables correspond to each of our three empirical expectations. First we code each INGO's issue area based on its mission statement reported in its registration documentation. Given there is certain level of subjectivity in the coding process, the coding of issue areas are cross-checked between the researchers---Author 1 assigned each organization into one of the issue areas defined in Article 3 of the ONGO Law, and Author 2 cross-checked the coding for ambiguous cases. We include our coding rules for overlapping issue areas in the appendix (in the future). We categorize each organization into one of the following nine issue areas:

-   **Economy and trade**
-   **Environment** (including animal protection)
-   **Education** (including youth development)
-   **Charity and humanitarian** poverty alleviation, disaster relief, etc., including rural development
-   **Science and technology**
-   **Industry association**
-   **Health**, public health and health care system support (professional training)
-   **Arts and Culture** including sports and international culture exchange
-   **General**, usually grant-making organizations, or working on general international communication, including among governments, or working on multiple fields not overlapping

Our second independent variable is a dichotomous indicator of whether the INGO explicitly states that it intends to operate locally (below province level). There are cases where the aim of the INGO is attached to a locality, either having a county or city name in their RO name or purposes, or the INGO are actually set up by people in China and they registered the RO to communicate between the "hometown" and the INGO set up abroad. We thus include this variable in our analysis to explore how having local connections is associated with the operational space of ROs.

Our final independent variable measures how much time elapsed between the January 1, 2017 (when the law took effect) and the organization's official registration date. There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect[@Shieh:2018]. This is largely because both INGOs and the regulators needed some transitional time to explore the specific implementation of the law as large ambiguity was left when the law was passed. We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there is no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic. (to find a citation for this, probably Spires, if there is one.)

## Modeling approach

Our data provides us with rich descriptive detail of the types of INGOs allowed to register in China following the advent of the ONGO law, and we explore patterns in this data below. In addition to presenting descriptive summary statistics, we create a multilevel Bayesian regression model to examine the complex effects that issue area, local connections, and registration timing have on organizational flexibility. This approach allows us to hold specific variables constant and generate predictions for hypothetical new, not-yet-registered INGOs, providing us with stronger empirical implications. Additionally, Bayesian modeling allows us to calculate the posterior distribution of our different estimands. Rather than report a single value for the proportion of registered INGOs worked on specific issues, we can estimate posterior credible intervals that represent the probability that the true proportion falls within a specific range. We report posterior medians and 95% credible intervals throughout our analysis. Importantly, these intervals do not behave like more traditional frequentist confidence intervals. Instead, they can be interpreted as the probability that a reported estimate falls within the range, given the data and modeling choices.

```{r fig-province-count-collapsed, fig.width=6, fig.height=3}
#| include: true
#| echo: false
#| fig-cap: "Count of the number of provinces each INGO is authorized to operate in. The left panel shows the full distribution of INGOs registered in 2–31 provinces; the right panel collapses these in-between counts to a single category."
provinces_collapsed <- ongo |> 
  drop_na(province_count) |> 
  mutate(province_count = case_when(
    province_count == 1 ~ "1",
    province_count > 1 & province_count < 32 ~ "2–31",
    province_count == 32 ~ "32"
  ))

p1 <- ggplot(ongo, aes(x = province_count)) +
  geom_histogram(binwidth = 1, linewidth = 0.1, boundary = 0,
                 fill = clrs[6], color = "white") +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  labs(x = "Provinces INGOs are authorized to work in", y = "Count") +
  theme_ongo()

p2 <- ggplot(provinces_collapsed, aes(x = province_count)) + 
  geom_bar(fill = clrs[6]) +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(sec.axis = sec_axis(trans = ~ . / nrow(provinces_collapsed),
                                         labels = label_percent()),
                     breaks = seq(0, 250, 50)) +
  labs(x = NULL, y = NULL) +
  theme_ongo()

(p1 | p2) + 
  plot_layout(nrow = 1, widths = c(0.7, 0.3))
```

Modeling the count of provinces each INGO is authorized to operate in presents a unique statistical challenge. As seen in @fig-province-count-collapsed, roughly 30% of INGOs are registered in only one province, 40% are registered nationwide, while the remaining 30% are registered in 2–31 provinces. Our main variable of interest is thus a mix of continuous outcomes (i.e. a range of provinces) bounded between two discrete outcomes (i.e. one province and all provinces). Standard modeling approaches like ordinary least squares regression (OLS) cannot accurately capture the unique features of the data and will generate predictions that fall outside allowable bounds (i.e. negative counts of provinces or more than 32 provinces). If we transform the count of provinces to a percentage, Beta regression would work well, as it is naturally limited to outcomes within a 0–1 range. However, Beta regression cannot handle values that are exactly 0 or 1, making it inappropriate for our data with its inflated counts at 0 (1) and 100% (32). To account for values at the bounds, we rely on ordered Beta regression [@Kubinec:2022], an extension of zero-and-one-inflated Beta regression that allows us to simultaneously model the continuous range of provinces (2–31) and the discrete outcomes (1 province and 32 provinces) without relying on percentages. We can thus explore the dynamics of each of our independent variables of interest in multiple ways—we can see (1) how each variable predicts that an organizations works in one province, nationwide, or somewhere in between, and (2) how each variable predicts the overall expected count of provinces.

@eq-ordbeta provides a formal definition of our modeling choices. Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables. We also include province-specific random offsets for each intercept to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus. We use weakly informative priors for all model parameters.

:::{.column-page-inset}
$$
\begin{aligned}
&\ \textbf{Registered provinces for INGO } i \\
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
&\ \textbf{Model of outcome average} \\
% Put the huge equation in a nested \begin{aligned}[t] environment so that 
% \mathrlap{} can go around it so that the annotations in the priors can be 
% aligned closer to the math
\mu_i =&\ 
  \mathrlap{\begin{aligned}[t]
  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
  \end{aligned}}\\[8pt]
&\ \textbf{Priors} \\
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
\end{aligned}
$$ {#eq-ordbeta}
:::

# Results

## Descriptive overview of data

Before examining the posterior results of our statistical model, we first describe some of the general trends in INGO registration during the first 5 years of the ONGO law. We use our data to explore (1) when INGOs registered, (2) what kinds of issues registered INGOs work on, and (3) how large of a geographic reach INGOs have.

First, @fig-registration-timeline shows the distribution of the count of new INGO registrations since January 1, 2017. A couple dozen organizations were able to register immediately after the law took effect during the first quarter of 2017, while hundreds more registered during the rest of that year. Nearly half of all currently-registered INGOs in China---48%---registered in 2017. After the initial first-year wave, the count of new registrations has declined slowly since 2018.

```{r fig-registration-timeline, fig.width=6, fig.height=3}
#| include: true
#| echo: false
#| fig-cap: "Count of international NGO registrations under the 2017 ONGO Law, divided by quarters"
ggplot(ongo, aes(x = registration_date)) +
  geom_histogram(binwidth = 365.25/4, boundary = ymd("2017-01-01"), 
                 fill = clrs[6], color = "white") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  labs(x = NULL, y = "Count of new INGO registrations") +
  theme_ongo()
```

Next, @fig-issue-props shows the distribution of issue areas that registered INGOs focus on. The two most common issues are economic, trade, and industry associations, representing 50% of all INGOs. Many of these organizations are bilateral chambers of commerce or other multilateral trade organizations such as the Japan-China Economic Association, the Silk Road Chamber of International Commerce, and the Canada China Business Council, and most are not more stereotypical international humanitarian organizations. Charitable, humanitarian, education, and health INGOs are far less common than their trade and industry counterparts. For instance, charity and humanitarian organizations like World Vision, Save the Children, and the Salvation Army comprise only 12% (73) of all INGOs.

```{r fig-issue-props, fig.width=6, fig.height=3}
#| include: true
#| echo: false
#| fig-cap: "Count of international NGO registrations, divided by issue area"
# TODO: Use issue_area instead of work_field_code
issue_count <- ongo |> 
  drop_na(work_field_code1) |> 
  group_by(work_field_code1) |>
  summarize(n = n()) |> 
  mutate(work_field_code1 = fct_reorder(work_field_code1, n))

ggplot(issue_count, aes(y = work_field_code1, x = n)) +
  geom_col(fill = clrs[5]) +
  scale_x_continuous(sec.axis = sec_axis(trans = ~ . / sum(issue_count$n),
                                         labels = label_percent())) +
  labs(x = "Count of INGOs", y = NULL) +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

Finally, there are clear geographic trends in INGO registration. As seen in @fig-home-office-map, the majority of INGOs are headquartered in Beijing (166), Shanghai (137), and Guangdong Province (46). INGOs must select a home office for their Chinese operations, but they are not necessarily limited to work within their home provinces. As described earlier, each INGO is authorized to work in a list of approved provinces, and the count provinces follows a unique three-level distribution, seen previously in @fig-province-count-collapsed, with 30% of INGOs authorized to work in just one province, 40% authorized to work nationally, and 30% authorized to work in a multiple provinces, but not in the whole country.

```{r fig-home-office-map}
#| include: true
#| echo: false
#| fig-cap: "Count of international NGO registrations, divided by issue area"
# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
ggplot() +
  geom_sf(data = ongo_mapdata, aes(fill = ro_count), 
          linewidth = 0.3, color = "white") +
  scale_fill_distiller(palette = "Reds", direction = 1, guide = "none") +
  geom_label_repel(data = filter(ongo_mapdata, ro_count > 0), 
                   aes(label = ro_count, geometry = geometry),
                   stat = "sf_coordinates", seed = 1234, label.size = 0.1, size = 3,
                   segment.color = "black", segment.size = 0.5, min.segment.length = 0) +
  coord_sf(crs = st_crs("EPSG:4480")) +  # China Geodetic Coordinate System 2000
  theme_void()
```

## Posterior predictions

Next we explore our data in more depth by generating and analyzing posterior predictions from our ordered Beta regression model, varying specific variables of interest while holding all others constant.

### Issue area

Following our first empirical expectation, we predict that INGOs working on less contentious issues should be registered in more provinces and have more geographic flexibility in operating throughout the country. To explore this, we can take advantage of the simultaneous continuous and discrete features of ordered Beta regression and see how often an INGO in each issue area is predicted to work in a single province, across all provinces, or some number in between. @fig-issue-preds-1 presents a summary of predicted posterior outcomes for 1,000 hypothetical INGOs, varying each possible issue area and holding all other variables at their mean or modal values. Several notable trends emerge from the model results. INGOs focused on arts and culture are overwhelming the most likely kind of organization to work nationally---arts and culture organizations are predicted to work in all 32 provinces 80% of the time (with a credible interval of 78--83%) and are only predicted to work in a single province a rare 3--5% of the time. Education-focused INGOs, on the other hand, are the least likely kind of organization to be registered in all 32 provinces and are predicted to do so only 32--38% of the time. Education INGOs are the most likely to be registered in only one province, with that predicted outcome appearing 24--29% of the time---at least 10 percentage points higher than any other issue area's predicted proportion. All other issue areas follow roughly the patterns in predictions: the most common outcome is for organizations to work nationally (50--60% of the time), followed by working in at least 2 provinces (25--40% of the time), followed by working in a single province (10--20% of the time). @fig-issue-preds-2 shows the continuous posterior distribution of the average number of provinces INGOs are expected to be registered in across all types of issue areas, but accounting for the 1- and 32-only provinces simultaneously. We can see a similar trend---arts and culture INGOs are predicted to work in 28--30 provinces on average, while education INGOs are only predicted to work in 12--20. All other issues range between 20--28 provinces.

```{r fig-issue-preds, fig.width=8, fig.height=6}
#| include: true
#| echo: false
#| column: body-outset
#| fig-cap: "*Top*: Posterior predictions from ordered Beta regression model,
#|   conditional on organization issue area, showing the predicted proportion of
#|   INGOs working in 1 province, all 32 provinces, or somewhere in between. The
#|   vertical slices of the bars depict 500 posterior samples; the fuzziness
#|   represents the uncertainty in category boundaries. 95% credible intervals 
#|   are shown as ranges in each category. *Bottom*: Expectation (or average) of
#|   posterior predictive distributions. These distributions take into account 
#|   single-province and nationwide predictions and represent the *overall*
#|   conditional average geographic range for INGOs. Points show posterior 
#|   median; lines show 80% and 95% credible intervals."
preds_issue_plot <- preds_issue |> 
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "Only 1 province",
    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
    .prediction == 1 ~ "All 32 provinces",
    .ptype = factor(
      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
      ordered = TRUE)
  )) |> 
  group_by(outcome, issue_area_nice, draw) |> 
  summarize(count = n()) |> 
  group_by(issue_area_nice, draw) |> 
  mutate(prop = count / sum(count))

preds_issue_plot_order <- preds_issue_plot |> 
  filter(outcome == "All 32 provinces") |>
  group_by(issue_area_nice) |> 
  summarize(median_prop = median(prop)) |> 
  arrange(median_prop) |> 
  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
  mutate(issue_area_nice = fct_inorder(issue_area_nice))

preds_issue_text <- preds_issue_plot |> 
  group_by(outcome, issue_area_nice) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  group_by(issue_area_nice) |> 
  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
  mutate(y_plot = 1 - y_plot) |> 
  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
  mutate(prop_ci_nice = glue::glue(
    "{ymin}–{ymax}",
    ymin = label_number(accuracy = 1, scale = 100)(ymin),
    ymax = label_percent(accuracy = 1)(ymax)
  )) |> 
  mutate(issue_area_nice = factor(
    issue_area_nice, 
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  ))

p1 <- preds_issue_plot |> 
  mutate(issue_area_nice = factor(
    issue_area_nice, 
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  )) |> 
  ggplot(aes(x = draw, y = prop)) +
  geom_col(aes(fill = outcome), position = "stack", linewidth = 0, width = 1) +
  geom_text(
    data = preds_issue_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
  labs(
    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
    title = "Predicted proportion of type of geographic reach across issue area",
    subtitle = "Posterior predictions of outcome categories"
  ) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

p2 <- epreds_issue |>
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |>
  mutate(issue_area_nice = factor(
    issue_area_nice,
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  )) |>
  ggplot(aes(x = issue_area_nice, y = prop_to_provinces(.epred))) +
  stat_halfeye(fill = clrs[6], color = clrs[8]) +
  scale_x_discrete(labels = NULL) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1, scales = "free_x") +
  guides(fill = "none") +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces",
    subtitle = "Expectation of posterior predictions"
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  theme_ongo() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

(p1 / plot_spacer() / p2) +
  plot_layout(heights = c(0.65, 0.02, 0.33))
```

As explained previously, we expect that the contentiousness of an NGO's issue area should influence its geographic reach and overall flexibility. No INGOs engaged in contentious issues like human rights advocacy have successfully registered in China, but there is some slight variation in the level of contention even among organizations working on less contentious issues like humanitarian assistance, health, and the environment. Education is particularly notable as the least flexible and most geographically restricted subsector. While education is typically considered a low-contention issue, in China fears of Western influence through educational institutions were an original impetus for the ONGO law. In 2006, an article in a CCP-owned newspaper warned that the growing presence of international NGOs would "undermine national security," "destroy political stability," "foster corruption," "propagate foreign practices," and "spy on and gather information on China's military, political, and economic information" [@Yin:2009, 534]. The idea that INGOs would "propagate foreign practices" had especially powerful salience, since increased exposure to the West through international NGOs had the potential to "lead to adoption of Western ideas of liberty, further endangering government control over the populace" [@HsiaWhite:2002, 337]. Educational NGOs were one particular avenue for the West to exert influence in the country---the directors and presidents of dozens of China's largest domestic NGOs have received doctoral degrees from and hold visiting appointments at Cornell, Duke, UNC-Chapel Hill, Harvard, Yale, and other prominent US universities [@Wang:2012, 108--9], and their training and connections abroad have influenced their programming and advocacy at home. In 2006, one Chinese NGO leader candidly explained that "foreign influence is definitely great. There is conceptual influence. Foreign NGOs' working methods also affect Chinese NGOs" [@Wang:2012, 110]. Education can thus be seen as one of the more contentious issues allowed under the ONGO law, and thus more closely regulated and restricted.

### Local connections

In our second empirical expectation, we posit that since INGOs that seek out local connections and that are focused on more local China-specific issues, those organizations should be registered in fewer provinces. The results from our model confirm this expectation. @fig-local-preds-1 shows the distribution of predicted posterior outcomes for 1,000 hypothetical INGOs. Organizations without local connections are predicted to work nationally across all provinces nearly half of the time (with a 95% credible interval of 46--51%), and are predicted to work in two or more provinces 32--37% of the time. These organizations with no local connections or local programmatic focus are only predicted to work in a single province 15--19% of the time. In contrast, INGOs *with* local connections are far more likely to only work in one province (32--38%), or only work in a handful of provinces (36--41%). For these locally-focused organizations, the least common prediction is to work nationally, with only a 23--29% probability. @fig-local-preds-2 shows the posterior distribution of the average number of provinces INGOs are expected to be registered in, conditional on their local connections. The same relationship holds---an INGO without local connections is predicted to work in 19--24 provinces on average, while an organization with local connections is only predicted to work in 8--17.

```{r fig-local-preds, fig.width=8, fig.height=4}
#| include: true
#| echo: false
#| fig-cap: "Posterior predictions from ordered Beta regression model, 
#|   conditional on having local connections. *Top*: Predicted proportion of 
#|   INGOs working in 1 province, all 32 provinces, or somewhere in between. 
#|   The vertical slices of the bars depict 500 posterior samples; the fuzziness 
#|   represents the uncertainty in category boundaries. 95% credible intervals 
#|   are shown as ranges in each category. *Bottom*: Expectation (or average) of 
#|   posterior predictive distributions. These distributions take into account 
#|   single-province and nationwide predictions and represent the *overall* 
#|   conditional average geographic range for INGOs. Points show posterior 
#|   median; lines show 80% and 95% credible intervals."
preds_local_plot <- preds_local |> 
  unnest(preds) |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "Only 1 province",
    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
    .prediction == 1 ~ "All 32 provinces",
    .ptype = factor(
      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
      ordered = TRUE)
  )) |> 
  group_by(outcome, local_connect, draw) |> 
  summarize(count = n()) |> 
  group_by(local_connect, draw) |> 
  mutate(prop = count / sum(count))

preds_local_text <- preds_local_plot |> 
  group_by(outcome, local_connect) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  group_by(local_connect) |> 
  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
  mutate(y_plot = 1 - y_plot) |> 
  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
  mutate(prop_ci_nice = glue::glue(
    "{ymin}–{ymax}",
    ymin = label_number(accuracy = 1, scale = 100)(ymin),
    ymax = label_percent(accuracy = 1)(ymax)
  ))

p1 <- preds_local_plot |> 
  ggplot(aes(x = draw, y = prop)) +
  geom_col(aes(fill = outcome), position = position_stack(), linewidth = 0, width = 1) +
  geom_text(
    data = preds_local_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1) +
  labs(
    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
    title = "Predicted proportion of type of\ngeographic reach across local connections",
    subtitle = "Posterior predictions of outcome categories"
  ) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

p2 <- epreds_local |>
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
  ggplot(aes(x = local_connect, y = prop_to_provinces(.epred))) +
  stat_halfeye(fill = clrs[6], color = clrs[8]) +
  scale_x_discrete(labels = NULL) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1, scales = "free_x") +
  guides(fill = "none") +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces",
    subtitle = "Expectation of posterior predictions"
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  theme_ongo() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

(p1 | p2) +
  plot_layout(widths = c(0.6, 0.4))
```

International NGOs with locally focused missions and connections with local provincial officials are thus far more likely to purposely limit their activities to specific provinces, while organizations with broader non-local missions have a larger geographic reach. While we cannot precisely tell which direction the causal story works with this phenomenon, we can make some reasonable speculations. It is likely that locally-oriented INGOs purposely network and seek out connections with local PSUs before formally registering, thus fostering better relationships with government officials and furthering the organization's mission within its limited provinces. It is also likely, given the high probability of national reach, that organizations without local connections purposely do not spend the time and effort to cultivate those relationships, as it is not necessary to operate across many provinces. A rival explanation that having local connections reduces an organization's flexibility does not seem warranted. Although INGOs with local connections do have a more limited geographic scope, INGOs appear to purposely limit the number of provinces they work in in order to focus more on their local work.

### Registration timing

The ONGO Law officially came into effect on January 1, 2017, and as seen previously in @fig-registration-timeline, the first year of the law saw the greatest total number of registrations. In our third empirical expectation, we propose that these early registrants under the new law were both less of a threat to regime stability and a higher priority for bureaucratic processing, and thus should be registered in more provinces and have more geographic flexibility throughout the country. However, the results of our model support the *reverse* of this expectation. @fig-timing-preds-1 once again shows the predicted posterior outcomes for 1,000 simulated INGOs across a range of time since January 2017. Organizations that registered in the first year are predicted to work in all provinces 41--46% of the time, and are predicted to work in two or more provinces 34--39% of the time. These early INGOs are the most likely to be registered in only one province and are predicted to do so 17--23% of the time. After the initial wave of registrations in 2017, the likelihood of nationwide reach steadily increases and replaces both the probability of a single province or a partial range of provinces. By the end of 2021---5 years after the ONGO Law took effect---the probability of national -level registration increases to 55--61% while the probability of working in a range of provinces increases to predicted to work in two or more provinces increase to 27--32%. These late INGOs are the least likely to be registered in only one province and are predicted to do so only 17--22% of the time. @fig-timing-preds-2 demonstrates the same results with the posterior distribution of the expected count of provinces over five years since 2017. INGOs that register early are predicted to work in 17--22 provinces, while those that wait until 2021 are predicted to work in 21--28.

```{r fig-timing-preds, fig.width=8, fig.height=4}
#| include: true
#| echo: false
#| fig-cap: "Posterior predictions from ordered Beta regression model, 
#|   conditional on time since law took effect in January 2017. *Top*: Predicted 
#|   proportion of INGOs working in 1 province, all 32 provinces, or somewhere 
#|   in between. Filled areas depict 50 posterior samples of the outcome category 
#|   probabilities, so the fuzziness represents the uncertainty in category 
#|   boundaries. *Bottom*: Expectation (or average) of posterior predictive 
#|   distributions. This distribution takes into account single-province and 
#|   nationwide predictions and represents the *overall* conditional average 
#|   geographic range for INGOs over time. Shaded regions show the 50%, 80%, 
#|   and 95% credible intervals."
preds_timing_plot <- preds_timing |> 
  unnest(preds) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "Only 1 province",
    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
    .prediction == 1 ~ "All 32 provinces",
    .ptype = factor(
      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
      ordered = TRUE)
  )) |> 
  mutate(years_since_law = 2017 + years_since_law) |> 
  group_by(outcome, years_since_law, draw) |>
  summarize(count = n()) |> 
  group_by(years_since_law) |> 
  mutate(prop = count / sum(count) * 100)

preds_timing_text <- preds_timing_plot |> 
  filter(years_since_law == 2017.2) |> 
  group_by(outcome) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
  mutate(y_plot = 1 - y_plot) |> 
  mutate(years_since_law = 2017.2)

layers <- preds_timing_plot |> 
  filter(draw <= 50) |> 
  split(~ draw) |> 
  lapply(\(x) {
    geom_area(
      data = x,
      aes(y = prop, fill = outcome),
      alpha = 0.1
    )
  })

p1 <- ggplot(preds_timing_plot, aes(x = years_since_law)) +
  layers +
  geom_text(
    data = preds_timing_text, 
    aes(y = y_plot, label = outcome),
    color = "white",
    hjust = 0, fontface = "bold", size = 3, show.legend = FALSE
  ) +
  scale_x_continuous(expand = expansion(mult = 0.02)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_color_manual(values = colorspace::darken(clrs[c(3, 5, 7)], 0.1)) +
  scale_fill_manual(values = colorspace::lighten(clrs[c(3, 5, 7)], 0)) +
  labs(
    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
    title = "Predicted proportion of type of \ngeographic reach since January 2017",
    subtitle = "Posterior predictions of outcome categories"
  ) +
  guides(fill = "none") +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank()
  )

p2 <- epreds_timing |>
  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
  stat_lineribbon(
    .width = c(0.5, 0.8, 0.95),
    alpha = 0.35, fill = clrs[6], color = clrs[6]
  ) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces",
    subtitle = "Expectation of posterior predictions"
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  theme_ongo()

p1 | p2
```


We lack sufficient theory or data to explain why this trend goes against our expectations, but we can again make reasonable speculations. As we saw previously with INGOs and local connections, organizations appear to strategically seek out the best avenues and methods for registering. Organizations that participated in the initial wave of registrations in 2017 likely had closer connections with local officials and were able to speed through the bureaucratic process registration more easily. As a preliminary test of this speculation, we rerun our main model with an interaction between years since registration and local connections to see how the effect of local connections changes over time. As seen in @fig-timing-local, early registrants in 2017 without local connections are more likely to have a larger geographic reach, registering in an average of 19--23 provinces, while their locally-focused counterparts are only expected to register in an average of 7--16 provinces. Accordingly, it may be that organizations with local connections are more likely to register early because of their pre-existing bureaucratic relationships, while organizations with a larger national reach take longer to undertake the registration process and thus register later. Further research on this point is warranted.

```{r fig-timing-local, fig.width=6, fig.height=3, out.width="80%"}
#| include: true
#| echo: false
#| fig-cap: "Expectation (or average) of posterior predictive distributions 
#|   from model with interaction between local connections and time since 
#|   January 2017. These predictions take into account single-province and 
#|   nationwide predictions and represent the overall conditional average 
#|   geographic range for INGOs over time across, conditional on local 
#|   connections. Shaded regions show the 50%, 80%, and 95% credible intervals"
epreds_timing_local |>
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
  stat_lineribbon(
    .width = c(0.5, 0.8, 0.95),
    alpha = 0.35, fill = clrs[6], color = clrs[6]
  ) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  guides(fill = "none") +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces across local connections",
    subtitle = "Expectation of posterior predictions"
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  facet_wrap(vars(local_connect)) +
  theme_ongo()
```


# Flexibility, contentiousness, and government relationships: The cases of Greenpeace and The Nature Conservancy

TODO: Meng - TA vs. RO, exploring main mechanisms of flexibility, contentiousness, and relationships


# Discussion and conclusion

TODO: Andrew: Not fully exploring the TA thing here - that's in another paper

::: callout-warning
**Still TODO!**
:::

# References
